### 2018-01-25 Text/paper.tex
Added latex template

\documentclass[a4paper,12pt]{article}
\title{An emperical study: How procastination fucks up people's lives}
\date{January 25, 2018}
\author{Lucas Fajidherbe, Daan Schrage and Ruben van der Ham\\\\
	\small Intelligent Systems\\
	\small Vrije Universiteit Amsterdam}

\begin{document}
\maketitle
\titlepage

\tableofcontents
\clearpage

\section*{Abstract}
abstract

\section{Introduction}

paperrrr

\section{Technical stuff}
XYZ 1010101010111

\end{document}

### 2018-01-25 bots/ml/ml.py

@@ -55,7 +55,7 @@ class Bot:
             # IMPLEMENT: Add a function call so that 'value' will
             # contain the predicted value of 'next_state'
             # NOTE: This is different from the line in the minimax/alphabeta bot
-            value = self.value(next_state)[0]
+            value = self.heuristic(next_state)
 
             if maximizing(state):
                 if value > best_value:

### 2018-01-25 bots/rdeep/rdeep.py

@@ -17,7 +17,7 @@ class Bot:
 	# How deep to sample
 	__depth = -1
 
-	def __init__(self, num_samples=2, depth=4):
+	def __init__(self, num_samples=4, depth=8):
 		self.__num_samples = num_samples
 		self.__depth = depth
 
@@ -41,7 +41,11 @@ class Bot:
 		for move in moves:
 			for s in range(self.__num_samples):
 
-				score = self.evaluate(state.next(move), player)
+				# If we are in an imperfect information state, make an assumption.
+
+				sample_state = state.make_assumption() if state.get_phase() == 1 else state
+
+				score = self.evaluate(sample_state.next(move), player)
 
 				if score > best_score:
 					best_score = score

### 2018-01-25 train-ml-bot.py

@@ -12,24 +12,26 @@ import sys
 import sklearn
 import sklearn.linear_model
 from sklearn.externals import joblib
+#from sklearn.externals.joblib import parallel
 
 from bots.rand import rand
-# from bots.rdeep import rdeep
+from bots.rdeep import rdeep
 
 from bots.ml.ml import features
 
 # How many games to play
-GAMES = 1000000
+GAMES = 10000
 
 # Which phase the game starts in
 PHASE = 1
 
 # The player we'll observe
-player = rand.Bot()
-# player = rdeep.Bot()
+#player = rand.Bot()
+player = rdeep.Bot()
 
 data = []
 target = []
+
 
 for g in range(GAMES):
 

### 2018-01-26 Text/paper.tex
Small tweaks in paper.tex
Added all section titles in paper.tex. Made a first draft of section 2: Background information.

@@
 \documentclass[a4paper,12pt]{article}
-\title{An emperical study: How procastination fucks up people's lives}
+\title{The benefits of an extended feature space in a machine learning bot for the game Schnapsen}
 \date{January 25, 2018}
-\author{Lucas Fajidherbe, Daan Schrage and Ruben van der Ham\\\\
+\author{Lucas Faijdherbe, Daan Schrage and Ruben van der Ham\\\\
 	\small Intelligent Systems\\
@@
 
-\section*{Abstract}
-abstract
+\begin{abstract}
+Abstract paragraph with abstract shit about abstract things
+\end{abstract}
 
 \section{Introduction}
+Introduction
 
-paperrrr
+\section{Background Information}
+\subsection{Schnapsen}
+Schnapsen is an Austrian card game, played with 20 cards; Only the Jacks, Queens, Kings, 10s and Aces are in the deck.
+The goal of the game is to win tricks, and to be the first player to score 66 points.
+Each game has a trump suit, which is determined randomly.
+A card from the trump suit lets you automatically win the trick, provided that there is no higher trump card in the game.
 
-\section{Technical stuff}
-XYZ 1010101010111
+The game has a multi-agent (we have an opponent), deterministic (the environment is determined by the current state and executed action), static (the environment does not change when an agent is choosing an action) and discrete (the game is turn-based) environment.
+The game consists of two phases: In phase one, when there are still cards in stock, we have an imperfect information game.
+In phase two, when the stock is depleted, we have a perfect information game, since we know exactly what the cards of our opponent are.
+The point count in the game is as follows: \\ \\
+\noindent
+\begin{tabular}{l l l l l}
+\textbf{J} & \textbf{Q} & \textbf{K} & \textbf{10} & \textbf{A} \\
+2 & 3 & 4 & 10 & 11 \\
+\end{tabular} \\
 
+\noindent
+A lot of points can also be won by marriages.
+If the player is leading the trick and has a king or a queen of the same suit, it can play one card, and show the other, so the opponent knows that there is a marriage.\\ \\
+\noindent
+\begin{tabular} {c c}
+\textbf{Normal marriage (non-trump suit)} & \textbf{Royal marriage (trump suit)} \\
+20 & 40 \\
+\end{tabular}\\
+
+\noindent
+The game starts in phase one, an imperfect-information game.
+Each agent has 5 cards.
+Player 1 plays a card, thereby determining the suit that has to be played.
+To win the trick, player 2 has to play a higher-ranking card from the same suit, or a trump card.
+Player 2 does not have to follow suit in phase 1, but he/she will lose the trick in that case.
+The winner of the trick now becomes player one and gets the cards, with the amount of points the two cards represent.
+This goes on until the stock is depleted; then we enter phase 2, a perfect-information game.
+Player 2 now has to follow suit.
+If it cannot do that, the player has to trump, and otherwise play any card.
+If a player reaches 66 points or more, the game is over.
+
+\subsection{Intelligent Systems Schnapsen Framework}
+The course provided us with a framework.
+We have an api, which is the skeleton for the Schnapsen game, and we have two scripts: one where we can let bots play against each other in a single game where we can see all the moves, and a script where we can play a tournament - with a specifiable number of the number of games to be played - and see how many games each bot has won.
+There are already multiple bots already present in the framework to play against:
+\begin{description}
+\item [Minimax / Alphabeta:] This bot only works in a perfect-information game (phase 2 of Schnapsen).
+It recursively looks through all the states, and decides what the best move to play will be, provided that the opponent plays optimally, and will try to minimize the outcome of the game for the player.
+\item [Bully:] Plays by a defined set of rules.
+If it has a trump card, it will play that.
+Otherwise, it will play a card of the same suit player 1 played.
+If it cannot do either of those things, it will play the highest ranking card of any suit.
+\item [Rand:] Chooses a random move out of all of the legal moves, and plays that.
+\item [Rdeep:] Functions quite like a Monte-Carlo sampling bot.
+It looks through multiple states, and averages the heuristics of a state, thereby ranking the moves.
+It then picks one of the highest ranking moves to play.
+\item [KBbot:] Logical reasoning bot. The strategy can be defined in propositional logic. The current strategy of the bot is to always play cheap cards (i.e kings, queens, jacks) first.
+\end{description}
+
+\subsection{Machine Learning Bots}
+For this paper, we will use machine learning bots with different set features to determine what the best features are.
+
+\section{Research Question}
+
+\section{Experimental setup}
+
+\section{Results}
+
+\section{Findings}
+
+\section{Conclusion}
 \end{document}

### 2018-01-26 Text/paper.tex
Added appendices sections

@@
 \documentclass[a4paper,12pt]{article}
+
+\usepackage{listings}
+
 \title{The benefits of an extended feature space in a machine learning bot for the game Schnapsen}
@@
 \section{Conclusion}
+
+\appendix
+\section{Worksheet I}
+\begin{enumerate}
+\item The \textit{rdeep} bot performs best, winning 20 out of 30 games. \\
+Output:
+\begin{lstlisting}[language=bash]
+Results:
+bot <bots.rand.rand.Bot instance at 0x101a70fc8>: 7 wins
+bot <bots.bully.bully.Bot instance at 0x101a71098>: 3 wins
+bot <bots.rdeep.rdeep.Bot instance at 0x101a71170>: 20 wins
+\end{lstlisting}
+
+\item The bully bot operates as follows:
+\begin{itemize}
+\item If it has a trump card, it will play that.
+\item If it does not have a trump card, it will play a card from the same suit
+\item If it cannot do either of those things, it will choose the highest ranking card of any suit.
+\end{itemize}
+\item Using this strategy means that you will try to get as many points as possible each move.
+However, this might also mean that early in the game, the bot will play valuable cards in order to get a high point ratio, but later in the game it has no good cards left.
+\item Have the bots complete a large number of tournaments (preferably n > 30), see if the rdeep bot still outperforms the rand bot, and how big the difference in wins is.
+If there is a significant difference, we can assume that rdeep is better than rand.
+\item Bot:
+\item The heat map:
+- Insert pdf here - This heatmap means:
+\item The added line:
+\begin{lstlisting}[language=bash]
+value, move = self.value(next_state, depth + 1)
+\end{lstlisting}
+Output:
+\begin{lstlisting}[language=bash]
+python tournament.py -p rand,minimax -s 2 -r 10
+Playing 10 games:
+Played 1 out of 10 games (10\%): [0, 1] 
+Played 2 out of 10 games (20\%): [0, 2] 
+Played 3 out of 10 games (30\%): [0, 3] 
+Played 4 out of 10 games (40\%): [0, 4] 
+Played 5 out of 10 games (50\%): [1, 4] 
+Played 6 out of 10 games (60\%): [2, 4] 
+Played 7 out of 10 games (70\%): [2, 5] 
+Played 8 out of 10 games (80\%): [3, 5] 
+Played 9 out of 10 games (90\%): [4, 5] 
+Played 10 out of 10 games (100\%): [4, 6] 
+Results:
+bot <bots.rand.rand.Bot instance at 0x102a70f80>: 4 wins
+bot <bots.minimax.minimax.Bot instance at 0x102a731b8>: 6 wins
+\end{lstlisting}
+\item
+\item The heuristic is a value between -1.0 and 1.0, derived from the point ratio of the current player.
+If the player has a 1.0 value, the player has a definite win.
+If the value is -1.0, the opponent has a definite win.
+\end{enumerate}
+\section{Worksheet II}
+\section{Worksheet III}
+
 \end{document}

### 2018-01-26 Text/paper.tex
Added some appendix things

@@
 \usepackage{listings}
+\usepackage{enumerate}
 
@@
 \begin{enumerate}
+
 \item The \textit{rdeep} bot performs best, winning 20 out of 30 games. \\
@@
 \end{itemize}
+
 \item Using this strategy means that you will try to get as many points as possible each move.
 However, this might also mean that early in the game, the bot will play valuable cards in order to get a high point ratio, but later in the game it has no good cards left.
+
 \item Have the bots complete a large number of tournaments (preferably n > 30), see if the rdeep bot still outperforms the rand bot, and how big the difference in wins is.
 If there is a significant difference, we can assume that rdeep is better than rand.
+
 \item Bot:
+
 \item The heat map:
 - Insert pdf here - This heatmap means:
+
 \item The added line:
@@
 Playing 10 games:
-Played 1 out of 10 games (10\%): [0, 1] 
-Played 2 out of 10 games (20\%): [0, 2] 
-Played 3 out of 10 games (30\%): [0, 3] 
-Played 4 out of 10 games (40\%): [0, 4] 
-Played 5 out of 10 games (50\%): [1, 4] 
-Played 6 out of 10 games (60\%): [2, 4] 
-Played 7 out of 10 games (70\%): [2, 5] 
-Played 8 out of 10 games (80\%): [3, 5] 
-Played 9 out of 10 games (90\%): [4, 5] 
-Played 10 out of 10 games (100\%): [4, 6] 
+Played 1 out of 10 games (10%): [0, 1] 
+Played 2 out of 10 games (20%): [0, 2] 
+Played 3 out of 10 games (30%): [0, 3] 
+Played 4 out of 10 games (40%): [0, 4] 
+Played 5 out of 10 games (50%): [1, 4] 
+Played 6 out of 10 games (60%): [2, 4] 
+Played 7 out of 10 games (70%): [2, 5] 
+Played 8 out of 10 games (80%): [3, 5] 
+Played 9 out of 10 games (90%): [4, 5] 
+Played 10 out of 10 games (100%): [4, 6] 
 Results:
@@
 \end{lstlisting}
+
 \item
+
 \item The heuristic is a value between -1.0 and 1.0, derived from the point ratio of the current player.
@@
 \section{Worksheet II}
+\begin{enumerate}
+\item The added clause that makes the knowledge base unsatisfiable:
+\begin{lstlisting}[language=bash]
+kb.add_clause(~B, ~C)
+\end{lstlisting}
+
+\item The three clauses converted to CNF:
+\begin{itemize}
+\item A V B
+\item -B V A
+\item -A V C
+\item -A V D
+\end{itemize}
+The code that creates the variables and the knowledge base:
+\begin{lstlisting}[language=bash]
+# Define our symbols
+A = Boolean('A')
+B = Boolean('B')
+C = Boolean('C')
+D = Boolean('D')
+
+# Create a new knowledge base
+kb = KB()
+
+# Add clauses
+kb.add_clause(A, B)
+kb.add_clause(~B, A)
+kb.add_clause(~A, C)
+kb.add_clause(~A, D)
+\end{lstlisting}
+Because the knowledge base entails A \& C \& D, all three have to be true. For now, the model has two solutions:
+\begin{lstlisting}[language=bash]
+{A: True, C: True, B: False, D: True}
+{A: True, C: True, B: True, D: True}
+\end{lstlisting}
+B can be whatever it wants, but A, B and D have to be true.
+
+\item Three constraints have to be met:
+\begin{enumerate}[I]
+\item $X = Y$
+\item $X + Y > 2$
+\item $X + Y < 5$
+\end{enumerate}
+The model is satisfiable, as long as: 
+$1 < x < 2.5$ and $1 < y < 2.5$
+
+\item We now have three models:
+\begin{lstlisting}[language=bash]
+(a) [x = y] = True, [x + y > 2] = True, [x + y < 5] = True
+(b) [x = y] = True, [x + y > 2] = True, [x + y < 5] = False
+(c) [x = y] = True, [x + y > 2] = False, [x + y < 5] = True
+\end{lstlisting}
+
+The three constraints per model: \\\\
+(a) This model already has three constraints. \\
+(b) Only the last clause has to change, namely to $[x + y >=5] $= True\\
+(c) Only the second clause has to change, namely to$ [x + y <= 2]$ = True.\\
+
+Now we end up with this:
+\begin{lstlisting}[language=bash]
+(a) [x = y] = True, [x + y > 2] = True, [x + y < 5] = True
+(b) [x = y] = True, [x + y > 2] = True, [x + y >= 5] = True
+(c) [x = y] = True, [x + y <= 2] = True, [x + y < 5] = True
+\end{lstlisting}
+
+\item What we want, is to find points on the line $x = y$, where the points either lie between $x + y > -5$ and $x + y < -2$, or where the points lie between $x + y > 2$ and $x + y < 5$.
+
+The clauses we need to add are:
+\begin{itemize}
+\item $x == y$
+\item $x + y > 2 V  x + y < -2$
+\item $x + y > -5 V  x + y < 5$
+\item $x + y > - 5 V  x + y > 2$
+\item $x + y < -2 V  x + y < 5$
+\end{itemize}
+
+The code:
+\begin{lstlisting}[language=bash]
+# Define our integer symbols
+x = Integer('x')
+y = Integer('y')
+
+q = x == y
+a = x + y > 2
+b = x + y < 5
+c = x + y < -2
+d = x + y > -5
+
+kb = KB()
+
+kb.add_clause(q)
+kb.add_clause(a, c)
+kb.add_clause(a, d)
+kb.add_clause(b, c)
+kb.add_clause(b, d)
+\end{lstlisting}
+
+\item
+
+\end{enumerate}
 \section{Worksheet III}
+\begin{enumerate}
+\item The added code:
+\begin{lstlisting}[language=bash]
+value = self.heuristic(next_state)
 
+p1_points = state.get_points(1)
+
+p2_points = state.get_points(2)
+
+p1_pending_points = state.get_pending_points(1)
+
+p2_pending_points = state.get_pending_points(2)
+
+trump_suit = state.get_trump_suit()
+
+phase = state.get_phase()
+
+stock_size = state.get_stock_size()
+
+leader = state.leader()
+
+whose_turn = state.whose_turn()
+
+opponents_played_card = state.get_opponents_played_card()
+\end{lstlisting}
+The result of the played tournament against rand and bully:
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102271290>: 16 wins
+bot <bots.rand.rand.Bot instance at 0x1022711b8>: 4 wins
+bot <bots.bully.bully.Bot instance at 0x1059b71b8>: 10 wins
+\end{lstlisting}
+
+\item We let the mlbot learn by playing against rdeep. But since the games took way longer than the games of mlbot vs rand, we set the number of games to 1000 (Which still took quite some time).
+
+We get a lower output now:
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102a73248>: 15 wins
+bot <bots.rand.rand.Bot instance at 0x102a73170>: 7 wins
+bot <bots.bully.bully.Bot instance at 0x10599df80>: 8 wins
+\end{lstlisting}
+
+ML now wins 15 times, where it won 16 times on the first tournament.
+This might have to do with the training set being smaller, and it was trained against rdeep, which does not compete in the tournament.
+However, the difference is not comparably worse.
+
+We decided to train the mlbot again against rdeep, but now with 5000 games. 
+Even after this long wait, the robot does not play significantly better or worse.
+
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102a71248>: 14 wins
+bot <bots.rand.rand.Bot instance at 0x102a71170>: 5 wins
+bot <bots.rdeep.rdeep.Bot instance at 0x105aa2cf8>: 11 wins
+\end{lstlisting}
+
+\end{enumerate}
 \end{document}

### 2018-01-30 Text/paper.tex
Added some stuff in paper.text

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[a4paper,11pt]{article}
 
@@
 \maketitle
-\titlepage
-
-\tableofcontents
 \clearpage
@@
 \section{Introduction}
-Introduction
+Artificial Intelligence is becoming a huge subject, and we see it appearing more and more in daily life: voice assistants on smartphones, self-driving Tesla's, AlphaGo defeating Go masters, and so on.
+...
+We can make a distinction between strong and weak AI [1]: \textit{weak AI} is focused on mastering problems in one limited area, whereas \textit{strong AI} is considered to be Artificial Intelligence with \textit{actual} intelligence, and even self-awareness.
+For this paper, we will be focussing on weak AI in games, more specifically in the game of Schnapsen.
+In section 2 we will describe Schnapsen in more detail, alongside the bots used for the game.
+The research question will be described in section 3.
+In section 4, we will talk more about the experiment.
+...
 
@@
 \subsection{Intelligent Systems Schnapsen Framework}
-The course provided us with a framework.
-We have an api, which is the skeleton for the Schnapsen game, and we have two scripts: one where we can let bots play against each other in a single game where we can see all the moves, and a script where we can play a tournament - with a specifiable number of the number of games to be played - and see how many games each bot has won.
+An API in Python has been provided, together with a framework for the Schnapsen game.
+Furthermore, we  have two scripts: one where bots can play against each other in a single game where all moves in the game can be seen, and a script where bots can play a tournament against each other - with a specifiable number of the number of games to be played - and where the number of won games per robot can be seen.
 There are already multiple bots already present in the framework to play against:
@@
 \section{Research Question}
+In our research, we want to find out if an extended feature space in a machine learning bot will improve its performance in Schnapsen.
+There is already a machine learning bot present, with what we will call, the \textit{default feature space}, provided by the framework.
+Our goal is to extend and improve this feature space, and see if the bot will have a better performance.
+Our hypothesis is that an extended feature space will lead to a better performance, since .....
+\\ \\
+\noindent
+The \textit{default feature space} contains the following features:
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\item Player 1's pending points
+\item Player 2's pending points
+\item The trump suit
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponenet
+\end{itemize}
 
 \section{Experimental setup}
+For the testing of the bots, multiple Schnapsen tournaments were held. Each bot played a 100 games against every other bot. The competing bots were:
+\begin{itemize}
+\item Minimax
+\item Bully
+\item Rand
+\item Rdeep
+\item KBBot
+\item ML
+\item MLAdvanced
+\end{itemize}
+
+Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.
 
@@
 \section{Conclusion}
+
+\section{References}
+1. http://humanparagon.com/strong-and-weak-ai/
 

### 2018-01-31 bots/mlAdvancedLucas/mlAdvanced.py
Added MLAdvanced bot

@@ -1,0 +1,188 @@
+#!/usr/bin/env python
+"""
+A basic adaptive bot. This is part of the third worksheet.
+
+"""
+
+from api import State, util, Deck
+import random, os
+
+from sklearn.externals import joblib
+
+# Path of the model we will use. If you make a model
+# with a different name, point this line to its path.
+DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
+
+class Bot:
+
+    __randomize = True
+
+    __model = None
+
+    def __init__(self, randomize=True, model_file=DEFAULT_MODEL):
+
+        print(model_file)
+        self.__randomize = randomize
+
+        # Load the model
+        self.__model = joblib.load(model_file)
+
+    def get_move(self, state):
+
+        val, move = self.value(state)
+
+        return move
+
+    def value(self, state):
+        """
+        Return the value of this state and the associated move
+        :param state:
+        :return: val, move: the value of the state, and the best move.
+        """
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+
+            # IMPLEMENT: Add a function call so that 'value' will
+            # contain the predicted value of 'next_state'
+            # NOTE: This is different from the line in the minimax/alphabeta bot
+            value = self.heuristic(next_state)
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+
+        return best_value, best_move
+
+    def heuristic(self, state):
+
+        # Convert the state to a feature vector
+        feature_vector = [features(state)]
+
+        # These are the classes: ('won', 'lost')
+        classes = list(self.__model.classes_)
+
+        # Ask the model for a prediction
+        # This returns a probability for each class
+        prob = self.__model.predict_proba(feature_vector)[0]
+
+        # Weigh the win/loss outcomes (-1 and 1) by their probabilities
+        res = -1.0 * prob[classes.index('lost')] + 1.0 * prob[classes.index('won')]
+
+        return res
+
+def maximizing(state):
+    """
+    Whether we're the maximizing player (1) or the minimizing player (2).
+    :param state:
[…]

### 2018-01-31 bots/mlAdvancedLucas/mlcopy.py
Added wrong bot. Changed bots

@@ -13,8 +13,8 @@ from sklearn.externals import joblib
 # with a different name, point this line to its path.
 DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
 
-class Bot:
 
+class Bot:
     __randomize = True
 
     __model = None
@@ -85,6 +85,7 @@ class Bot:
 
         return res
 
+
 def maximizing(state):
     """
     Whether we're the maximizing player (1) or the minimizing player (2).
@@ -130,9 +131,18 @@ def features(state):
     p1_pending_points = state.get_pending_points(1)
     feature_set.append(p1_pending_points)
 
-    # Add plauer 2's pending points to feature set
+    # Add player 2's pending points to feature set
     p2_pending_points = state.get_pending_points(2)
     feature_set.append(p2_pending_points)
+
+    # Difference between points
+    point_difference = abs(max(p1_points, p2_points) - min(p1_points, p2_points))
+    feature_set.append(point_difference)
+
+    # Difference between pending points
+    pending_point_difference = abs(
+        max(p1_pending_points, p2_pending_points) - min(p1_pending_points, p2_pending_points))
+    feature_set.append(pending_point_difference)
 
     # Get trump suit
     trump_suit = state.get_trump_suit()
@@ -143,9 +153,36 @@ def features(state):
     trump_suit_id = suits.index(trump_suit)
     feature_set.append(trump_suit_id)
 
+    # Trump card ratio:
+    cards = state.hand()
+    trump_card_count = 0
+    for card in cards:
+        if Deck.get_suit(cards[0]) == state.get_trump_suit():
+            trump_card_count += 1
+    if trump_card_count != 0:
+        trump_card_count = (trump_card_count / len(state.hand())) * 100
+    feature_set.append(trump_card_count)
+
+    # High ranking cards ratio:
+    high_rank_count = 0
+    for card in cards:
+        if Deck.get_rank(cards[0]) == "A" or Deck.get_rank(cards[0]) == "10":
+            high_rank_count += 1
+    if high_rank_count != 0:
+        high_rank_count = (high_rank_count / len(state.hand())) * 100
+    feature_set.append(high_rank_count)
+
     # Add phase to feature set
     phase = state.get_phase()
     feature_set.append(phase)
+
+    # Number of trump cards in phase 2:
+    phase2_trump_cards = 0
+    if phase == 2:
+        phase2_trump_cards = trump_card_count ** 2
[…]

### 2018-01-31 bots/ml_advanced/ml_advanced.py
Removed tournament's annoying dots and training scripts for each bot

@@ -1,0 +1,180 @@
+#!/usr/bin/env python
+"""
+A basic adaptive bot. This is part of the third worksheet.
+
+"""
+
+from api import State, util
+import random, os
+
+from sklearn.externals import joblib
+
+# Path of the model we will use. If you make a model
+# with a different name, point this line to its path.
+DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
+
+class Bot:
+
+    __randomize = True
+
+    __model = None
+
+    def __init__(self, randomize=True, model_file=DEFAULT_MODEL):
+
+        print(model_file)
+        self.__randomize = randomize
+
+        # Load the model
+        self.__model = joblib.load(model_file)
+
+    def get_move(self, state):
+
+        val, move = self.value(state)
+
+        return move
+
+    def value(self, state):
+        """
+        Return the value of this state and the associated move
+        :param state:
+        :return: val, move: the value of the state, and the best move.
+        """
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+
+            # IMPLEMENT: Add a function call so that 'value' will
+            # contain the predicted value of 'next_state'
+            # NOTE: This is different from the line in the minimax/alphabeta bot
+            value = self.heuristic(next_state)
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+
+        return best_value, best_move
+
+    def heuristic(self, state):
+
+        # Convert the state to a feature vector
+        feature_vector = [features(state)]
+
+        # These are the classes: ('won', 'lost')
+        classes = list(self.__model.classes_)
+
+        # Ask the model for a prediction
+        # This returns a probability for each class
+        prob = self.__model.predict_proba(feature_vector)[0]
+
+        # Weigh the win/loss outcomes (-1 and 1) by their probabilities
+        res = -1.0 * prob[classes.index('lost')] + 1.0 * prob[classes.index('won')]
+
+        return res
+
+def maximizing(state):
+    """
+    Whether we're the maximizing player (1) or the minimizing player (2).
+    :param state:
+    :return:
[…]

### 2018-01-31 bots/ml_lucas/ml_lucas.py

@@ -1,0 +1,230 @@
+#!/usr/bin/env python
+"""
+A basic adaptive bot. This is part of the third worksheet.
+
+"""
+
+from api import State, util, Deck
+import random, os
+
+from sklearn.externals import joblib
+
+# Path of the model we will use. If you make a model
+# with a different name, point this line to its path.
+DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
+
+
+class Bot:
+    __randomize = True
+
+    __model = None
+
+    def __init__(self, randomize=True, model_file=DEFAULT_MODEL):
+
+        print(model_file)
+        self.__randomize = randomize
+
+        # Load the model
+        self.__model = joblib.load(model_file)
+
+    def get_move(self, state):
+
+        val, move = self.value(state)
+
+        return move
+
+    def value(self, state):
+        """
+        Return the value of this state and the associated move
+        :param state:
+        :return: val, move: the value of the state, and the best move.
+        """
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+
+            # IMPLEMENT: Add a function call so that 'value' will
+            # contain the predicted value of 'next_state'
+            # NOTE: This is different from the line in the minimax/alphabeta bot
+            value = self.heuristic(next_state)
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+
+        return best_value, best_move
+
+    def heuristic(self, state):
+
+        # Convert the state to a feature vector
+        feature_vector = [features(state)]
+
+        # These are the classes: ('won', 'lost')
+        classes = list(self.__model.classes_)
+
+        # Ask the model for a prediction
+        # This returns a probability for each class
+        prob = self.__model.predict_proba(feature_vector)[0]
+
+        # Weigh the win/loss outcomes (-1 and 1) by their probabilities
+        res = -1.0 * prob[classes.index('lost')] + 1.0 * prob[classes.index('won')]
+
+        return res
+
+
+def maximizing(state):
+    """
[…]

### 2018-01-31 bots/ml_minimal/ml_minimal.py

@@ -1,0 +1,171 @@
+#!/usr/bin/env python
+"""
+A basic adaptive bot. This is part of the third worksheet.
+
+"""
+
+from api import State, util
+import random, os
+
+from sklearn.externals import joblib
+
+# Path of the model we will use. If you make a model
+# with a different name, point this line to its path.
+DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
+
+class Bot:
+
+    __randomize = True
+
+    __model = None
+
+    def __init__(self, randomize=True, model_file=DEFAULT_MODEL):
+
+        print(model_file)
+        self.__randomize = randomize
+
+        # Load the model
+        self.__model = joblib.load(model_file)
+
+    def get_move(self, state):
+
+        val, move = self.value(state)
+
+        return move
+
+    def value(self, state):
+        """
+        Return the value of this state and the associated move
+        :param state:
+        :return: val, move: the value of the state, and the best move.
+        """
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+
+            # IMPLEMENT: Add a function call so that 'value' will
+            # contain the predicted value of 'next_state'
+            # NOTE: This is different from the line in the minimax/alphabeta bot
+            value = self.heuristic(next_state)
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+
+        return best_value, best_move
+
+    def heuristic(self, state):
+
+        # Convert the state to a feature vector
+        feature_vector = [features(state)]
+
+        # These are the classes: ('won', 'lost')
+        classes = list(self.__model.classes_)
+
+        # Ask the model for a prediction
+        # This returns a probability for each class
+        prob = self.__model.predict_proba(feature_vector)[0]
+
+        # Weigh the win/loss outcomes (-1 and 1) by their probabilities
+        res = -1.0 * prob[classes.index('lost')] + 1.0 * prob[classes.index('won')]
+
+        return res
+
+def maximizing(state):
+    """
+    Whether we're the maximizing player (1) or the minimizing player (2).
+    :param state:
+    :return:
+    """
[…]

### 2018-01-31 tournament.py

@@ -46,7 +46,7 @@ def run_tournament(options):
                 wins[winner] += 1
 
             playedgames += 1
-            print('Played {} out of {:.0f} games ({:.0f}%): {} \r'.format(playedgames, totalgames, playedgames/float(totalgames) * 100, wins))
+            #print('Played {} out of {:.0f} games ({:.0f}%): {} \r'.format(playedgames, totalgames, playedgames/float(totalgames) * 100, wins))
 
     print('Results:')
     for i in range(len(bots)):

### 2018-01-31 train-ml_advanced-bot.py

@@ -22,7 +22,7 @@ from bots.ml import ml
 
 #Pick the features of which bot you want to use for training the model:
 from bots.ml.ml import features
-#from bots.ml_advanced.ml_advanced import features
+from bots.ml_advanced.ml_advanced import features
 # How many games to play
 GAMES = 10000
 
@@ -90,7 +90,7 @@ for str in target:
 print('instances per class: {}'.format(count))
 
 # Store the model in the ml directory
-joblib.dump(model, './bots/ml/model.pkl')
-#joblib.dump(model, './bots/ml_advanced/model.pkl')
+#joblib.dump(model, './bots/ml/model.pkl')
+joblib.dump(model, './bots/ml_advanced/model.pkl')
 
 print('Done')

### 2018-01-31 train-ml_lucas-bot.py

@@ -21,8 +21,8 @@ from bots.ml_advanced import ml_advanced
 from bots.ml import ml
 
 #Pick the features of which bot you want to use for training the model:
-from bots.ml.ml import features
-#from bots.ml_advanced.ml_advanced import features
+#from bots.ml.ml import features
+from bots.ml_lucas.ml_lucas import features
 # How many games to play
 GAMES = 10000
 
@@ -90,7 +90,7 @@ for str in target:
 print('instances per class: {}'.format(count))
 
 # Store the model in the ml directory
-joblib.dump(model, './bots/ml/model.pkl')
-#joblib.dump(model, './bots/ml_advanced/model.pkl')
+#joblib.dump(model, './bots/ml/model.pkl')
+joblib.dump(model, './bots/ml_lucas/model.pkl')
 
 print('Done')

### 2018-01-31 train-ml_minimal-bot.py

@@ -21,8 +21,8 @@ from bots.ml_advanced import ml_advanced
 from bots.ml import ml
 
 #Pick the features of which bot you want to use for training the model:
-from bots.ml.ml import features
-#from bots.ml_advanced.ml_advanced import features
+#from bots.ml.ml import features
+from bots.ml_minimal.ml_minimal import features
 # How many games to play
 GAMES = 10000
 
@@ -90,7 +90,7 @@ for str in target:
 print('instances per class: {}'.format(count))
 
 # Store the model in the ml directory
-joblib.dump(model, './bots/ml/model.pkl')
+joblib.dump(model, './bots/ml_minimal/model.pkl')
 #joblib.dump(model, './bots/ml_advanced/model.pkl')
 
 print('Done')

### 2018-01-31 Text/paper.tex
added combined bot

@@
 \section{Experimental setup}
-For the testing of the bots, multiple Schnapsen tournaments were held. Each bot played a 100 games against every other bot. The competing bots were:
+To answer our research question, multiple Schnapsen tournaments were held.
+Each machine-learning bot played multiple 120 game tournaments against each individual non-learning bot.
+Each learning bot played 9 tournaments with 3 different models against each static bot.
+The non-machine learning opponents were:
  \begin{itemize}
-\item Minimax
 \item Bully
@@
 \item Rdeep
-\item KBBot
-\item ML
-\item MLAdvanced
+\end{itemize}
+The research procedure was as follows:
+\begin{itemize}
+\item Training
+\item 120 game tournament
+\item 120 game tournament
+\item 120 game tournament
 \end{itemize}
 
+This procedure was repeated twice to reach the total of 9 tournaments respectively. The machine-learning bots did not compete against eachother.
 Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.

### 2018-01-31 bots/ml_combined/ml_combined.py

@@ -122,18 +122,26 @@ def features(state):
     # Add player 1's points to feature set
     p1_points = state.get_points(1)
     feature_set.append(p1_points)
+    feature_set.append(p1_points**2)
+    feature_set.append(p1_points**3)
 
     # Add player 2's points to feature set
     p2_points = state.get_points(2)
     feature_set.append(p2_points)
+    feature_set.append(p2_points**2)
+    feature_set.append(p2_points**3)
 
     # Add player 1's pending points to feature set
     p1_pending_points = state.get_pending_points(1)
     feature_set.append(p1_pending_points)
+    feature_set.append(p1_pending_points**2)
+    feature_set.append(p1_pending_points**3)
 
-    # Add player 2's pending points to feature set
+    # Add plauer 2's pending points to feature set
     p2_pending_points = state.get_pending_points(2)
     feature_set.append(p2_pending_points)
+    feature_set.append(p2_pending_points**2)
+    feature_set.append(p2_pending_points**3)
 
     # Difference between points
     point_difference = abs(max(p1_points, p2_points) - min(p1_points, p2_points))

### 2018-01-31 train-ml_combined-bot.py

@@ -1,0 +1,96 @@
+"""
+Train a machine learning model for the classifier bot. We create a player, and watch it play games against itself.
+Every observed state is converted to a feature vector and labeled with the eventual outcome
+(-1.0: player 2 won, 1.0: player 1 won)
+
+This is part of the second worksheet.
+"""
+from api import State, util
+
+# This package contains various machine learning algorithms
+import sys
+import sklearn
+import sklearn.linear_model
+from sklearn.externals import joblib
+#from sklearn.externals.joblib import parallel
+
+from bots.rand import rand
+from bots.rdeep import rdeep
+from bots.bully import bully
+from bots.ml_advanced import ml_advanced
+from bots.ml import ml
+
+#Pick the features of which bot you want to use for training the model:
+from bots.ml_combined.ml_combined import features
+#from bots.ml_advanced.ml_advanced import features
+# How many games to play
+GAMES = 10000
+
+# Which phase the game starts in
+PHASE = 1
+
+# The player we'll observe
+#player = rand.Bot()
+player = rdeep.Bot()
+#player = ml_advanced.Bot()
+
+data = []
+target = []
+
+
+for g in range(GAMES):
+
+    # Randomly generate a state object starting in specified phase.
+    state = State.generate(phase=PHASE)
+
+    state_vectors = []
+
+    while not state.finished():
+
+        # Give the state a signature if in phase 1, obscuring information that a player shouldn't see.
+        given_state = state.clone(signature=state.whose_turn()) if state.get_phase() == 1 else state
+
+        # Add the features representation of a state to the state_vectors array
+        state_vectors.append(features(given_state))
+
+        # Advance to the next state
+        move = player.get_move(given_state)
+        state = state.next(move)
+
+    winner, score = state.winner()
+
+    for state_vector in state_vectors:
+        data.append(state_vector)
+
+        if winner == 1:
+            result = 'won'
+
+        elif winner == 2:
+            result = 'lost'
+
+        target.append(result)
+
+    #sys.stdout.write(".")
+    sys.stdout.flush()
+    if g % (GAMES/20) == 0:
+        print("")
+        print('game {} finished ({}%)'.format(g, (g/float(GAMES)*100)))
+
+# Train a logistic regression model
+learner = sklearn.linear_model.LogisticRegression()
+model = learner.fit(data, target)
+
+# Check for class imbalance
+count = {}
+for str in target:
+    if str not in count:
[…]

### 2018-01-31 bots/ml_stripped/ml_stripped.py
Added results excel sheet and added stripped bot

@@ -1,0 +1,131 @@
+#!/usr/bin/env python
+"""
+A basic adaptive bot. This is part of the third worksheet.
+
+"""
+
+from api import State, util
+import random, os
+
+from sklearn.externals import joblib
+
+# Path of the model we will use. If you make a model
+# with a different name, point this line to its path.
+DEFAULT_MODEL = os.path.dirname(os.path.realpath(__file__)) + '/model.pkl'
+
+class Bot:
+
+    __randomize = True
+
+    __model = None
+
+    def __init__(self, randomize=True, model_file=DEFAULT_MODEL):
+
+        print(model_file)
+        self.__randomize = randomize
+
+        # Load the model
+        self.__model = joblib.load(model_file)
+
+    def get_move(self, state):
+
+        val, move = self.value(state)
+
+        return move
+
+    def value(self, state):
+        """
+        Return the value of this state and the associated move
+        :param state:
+        :return: val, move: the value of the state, and the best move.
+        """
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+
+            # IMPLEMENT: Add a function call so that 'value' will
+            # contain the predicted value of 'next_state'
+            # NOTE: This is different from the line in the minimax/alphabeta bot
+            value = self.heuristic(next_state)
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+
+        return best_value, best_move
+
+    def heuristic(self, state):
+
+        # Convert the state to a feature vector
+        feature_vector = [features(state)]
+
+        # These are the classes: ('won', 'lost')
+        classes = list(self.__model.classes_)
+
+        # Ask the model for a prediction
+        # This returns a probability for each class
+        prob = self.__model.predict_proba(feature_vector)[0]
+
+        # Weigh the win/loss outcomes (-1 and 1) by their probabilities
+        res = -1.0 * prob[classes.index('lost')] + 1.0 * prob[classes.index('won')]
+
+        return res
+
+def maximizing(state):
+    """
+    Whether we're the maximizing player (1) or the minimizing player (2).
+    :param state:
+    :return:
+    """
+    return state.whose_turn() == 1
+
+
+def features(state):
[…]

### 2018-01-31 train-ml_advanced-bot.py

@@ -31,7 +31,8 @@ PHASE = 1
 
 # The player we'll observe
 #player = rand.Bot()
-player = rdeep.Bot()
+#player = rdeep.Bot()
+player = bully.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-01-31 train-ml_stripped-bot.py

@@ -22,7 +22,7 @@ from bots.ml import ml
 
 #Pick the features of which bot you want to use for training the model:
 #from bots.ml.ml import features
-from bots.ml_minimal.ml_minimal import features
+from bots.ml_stripped.ml_stripped import features
 # How many games to play
 GAMES = 10000
 
@@ -31,8 +31,7 @@ PHASE = 1
 
 # The player we'll observe
 #player = rand.Bot()
-#player = rdeep.Bot()
-player = bully.Bot()
+player = rdeep.Bot()
 #player = ml_advanced.Bot()
 
 data = []
@@ -91,7 +90,7 @@ for str in target:
 print('instances per class: {}'.format(count))
 
 # Store the model in the ml directory
-joblib.dump(model, './bots/ml_minimal/model.pkl')
-#joblib.dump(model, './bots/ml_advanced/model.pkl')
+#joblib.dump(model, './bots/ml/model.pkl')
+joblib.dump(model, './bots/ml_stripped/model.pkl')
 
 print('Done')

### 2018-01-31 Text/paper.tex
Finished adding data to rdeep and rand

@@
 \section{Experimental setup}
+
+WORK IN PROGRESSSS
+
 To answer our research question, multiple Schnapsen tournaments were held.
-Each machine-learning bot played multiple 120 game tournaments against each individual non-learning bot.
-Each learning bot played 9 tournaments with 3 different models against each static bot.
-The non-machine learning opponents were:
- \begin{itemize}
-\item Bully
-\item Rand
-\item Rdeep
-\end{itemize}
+Each learning bot played multiple 120 game tournaments against each individual non-learning bot.
+Each learning bot played a total of 9 tournaments with 3 different models against each static bot.
+\subsection{The bots}
+The non- learning opponents were Rand, Bully and Rdeep. The learning components we created were:
+\begin{description}
+\item [ml\_minimal:] asdf
+\item [ml\_stripped:]  asdf
+\item [ml:] This ml bot is provided by the framework and consists of the  \textit{default feature space} 
+\item [ml\_enriched:]  asdf
+\item [ml\_advanced:] asdf
+\end{description}
+
 The research procedure was as follows:

### 2018-01-31 train-ml_combined-bot.py

@@ -24,14 +24,14 @@ from bots.ml import ml
 from bots.ml_combined.ml_combined import features
 #from bots.ml_advanced.ml_advanced import features
 # How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
 PHASE = 1
 
 # The player we'll observe
-#player = rand.Bot()
-player = rdeep.Bot()
+player = rand.Bot()
+#player = rdeep.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-01-31 train-ml_stripped-bot.py

@@ -24,14 +24,14 @@ from bots.ml import ml
 #from bots.ml.ml import features
 from bots.ml_stripped.ml_stripped import features
 # How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
 PHASE = 1
 
 # The player we'll observe
-#player = rand.Bot()
-player = rdeep.Bot()
+player = rand.Bot()
+#player = rdeep.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-01-31 Text/paper.tex
Changed a lot of things

@@
 \section{Research Question}
-In our research, we want to find out if an extended feature space in a machine learning bot will improve its performance in Schnapsen.
-There is already a machine learning bot present, with what we will call, the \textit{default feature space}, provided by the framework.
-Our goal is to extend and improve this feature space, and see if the bot will have a better performance.
-Our hypothesis is that an extended feature space will lead to a better performance, since .....
-\\ \\
+In our research, we want to find what feature set will improve the machine learning bot's performance the most in Schnapsen.
+There is already a machine learning bot present, which acts as a base line - with what we will call, the \textit{default feature space}- provided by the framework.
+\\
+
 \noindent
@@
 \item Whose turn it is currently
-\item The played card of the opponenet
+\item The played card of the opponent
 \end{itemize}
+
+\noindent
+Our goal is to build multiple bots machine learning bots, both with extended feature spaces and narrower feature spaces, and see which bot will perform best.
+With \textit{performs best}, we mean which bot will have the most wins against the other bots (rdeep, bully, rand, minimax, kbbot).
+Our hypothesis is that the bots with an extended feature space will outperform the bots with a narrower feature space.
+The default machine-learning bot will probably lie somewhere in the middle of the bots in terms of performance.
+
+\section{Machine Learning Bots Feature Space}
+For the purpose of our research, we created 5 machine-learning bots accompanying the original machine-learning bot.
+Below, we will give an overview of the bots and the changes made.
+For the whole overview, refer to appendix A:
+
+\subsection{ ml\_stripped}
+This bot stripped-down version of the original ml-bot. Its feature space only contains the perspective, and the point count of both player 1 and player 2.
+
+\subsection{ml\_minimal}
+...
+
+\subsection{ml\_advancedSimple}
+This bot has a slightly extended feature space in comparison to the original ml-bot.
+The added features are player 1 and player 2 points are squared and cubed and added to the feature space.
+The same goes for the pending points, these are also squared and cubed, and added to the feature space, in order to get more of a difference in the data points.
+
+\subsection{ml\_advanced}
+This bot has a more extended feature space.
+Added are differences between points, differences between pending points, trump card ratio in the hand, high-ranking card ratio (10's or A's) in the hand, number of trump cards in phase 2, number of same suit cards as opponent's played card, and number of points currently in the hand $^2$.
+
+\subsection{ml\_combined} 
+The ml-combined bot combines, the advancedSimple and advanced ml-bot, creating a bot with all feature space extensions.
 
@@
 
-\appendix
+appendix
+\section{Overview of machine-learning bots' feature spaces}
+\subsection{ml\_stripped}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\end{itemize}
+\subsection{ml\_minimal}
+\subsection{ml\_advancedSimple}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 1's point count squared
+\item Player 1's point count cubed
+\item Player 2's point count
+\item Player 2's point count squared
+\item Player 2's point count cubed
+\item Player 1's pending points
+\item Player 1's pending points squared
+\item Player 1's pending points cubed
+\item Player 2's pending points
+\item Player 2's pending points squared
+\item Player 2's pending points cubed
+\item The trump suit
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\end{itemize}
+\subsection{ml\_advanced}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\item Player 1's pending points
+\item Player 2's pending points
+\item Difference between player 1 and player 2's point count
+\item Difference between player 1 and player 2's pending point count
+\item The trump suit
+\item Trump card ratio (Number of trump cards in hand / total number of cards in hand * 100)
+\item High-ranking card ratio (Number of 10's and A's in hand / total number of cards in hand * 100)
+\item The phase
+\item Number of trump cards in hand in phase 2
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\item Number of cards in same suit as opponent's played suit in hand.
+\item Number of points in hand squared ($card1^2$ + $card2^2$ ...)
+\end{itemize}
+
+\subsection{ml\_combined}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 1's point count squared
+\item Player 1's point count cubed
+\item Player 2's point count
+\item Player 2's point count squared
+\item Player 2's point count cubed
+\item Player 1's pending points
+\item Player 1's pending points squared
+\item Player 1's pending points cubed
+\item Player 2's pending points
+\item Player 2's pending points squared
+\item Player 2's pending points cubed
+\item Difference between player 1 and player 2's point count
+\item Difference between player 1 and player 2's pending point count
+\item The trump suit
+\item Trump card ratio (Number of trump cards in hand / total number of cards in hand * 100)
+\item High-ranking card ratio (Number of 10's and A's in hand / total number of cards in hand * 100)
+\item The phase
+\item Number of trump cards in hand in phase 2
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\item Number of cards in same suit as opponent's played suit in hand.
+\item Number of points in hand squared ($card1^2$ + $card2^2$ ...)
+\end{itemize}
+
 \section{Worksheet I}

### 2018-01-31 Text/paper.tex
Updated Experimental setup (still WIP)

--- 2018-01-31 Text/paper.tex
@@
 An API in Python has been provided, together with a framework for the Schnapsen game.
-Furthermore, we  have two scripts: one where bots can play against each other in a single game where all moves in the game can be seen, and a script where bots can play a tournament against each other - with a specifiable number of the number of games to be played - and where the number of won games per robot can be seen.
-There are already multiple bots already present in the framework to play against:
+Furthermore, we  have two scripts: one where bots can play against each other in a single game where all moves in the game can be seen, and a script where bots play a tournament against each other - with a specifiable number of games to be played - and where the number of won games per robot can be seen.
+There are already multiple bots present in the framework to play against:
 \begin{description}
@@
 \subsection{Machine Learning Bots}
-For this paper, we will use machine learning bots with different set features to determine what the best features are.
+For this paper, we will use machine learning bots with different sets of features to determine what the best features are.
 
@@
 
-WORK IN PROGRESSSS
+To answer our research question, multiple Schnapsen tournaments were held. Each learning bot played multiple 120 game tournaments against each individual non-learning bot.
 
-To answer our research question, multiple Schnapsen tournaments were held.
-Each learning bot played multiple 120 game tournaments against each individual non-learning bot.
-Each learning bot played a total of 9 tournaments with 3 different models against each static bot.
 \subsection{The bots}
-The non- learning opponents were Rand, Bully and Rdeep. The learning components we created were:
+The non- learning opponents were Rand, Bully and Rdeep. The learning bots we created were:
 \begin{description}
-\item [ml\_minimal:] asdf
-\item [ml\_stripped:]  asdf
+\item [ml\_minimal:] This bot has only the perspective and both players points as features.
+
+\item [ml\_stripped:] ml\_stripped has all the \textit{default feature space} except for both players pending points and trumpsuit id.
+
 \item [ml:] This ml bot is provided by the framework and consists of the  \textit{default feature space}
-\item [ml\_enriched:]  asdf
-\item [ml\_advanced:] asdf
+
+\item [ml\_enriched:]  This bot has all the features of ml bot. In addition to the \textit{default feature space} the following features were added to the feature space:
+\begin{itemize}
+\item Both player's points squared
+\item Both player's pending points squared
+\item Both player's points cubed
+\item Both player's pending points cubed
+\end{itemize}
+
+\item [ml\_advanced:] ml\_advanced  has the following features in addition to the \textit{default feature space}:
+\begin{itemize}
+\item Difference between points
+\item Difference between pending points
+\item Trump card ratio in hand
+\item High card ratio in hand (10/A's)
+\item Number of trump cards in hand in phase 2
+\item Number of cards with same suit as opponents played suit
+\item Number of points in hand (squared)
+\end{itemize}
 \end{description}
 
-The research procedure was as follows:
+\subsection{The testing procedure}
+
+Each learning bot played a total of 9 tournaments with 3 different models against each non-learning bot.
+The testing procedure was as follows:
 \begin{itemize}
 \item Training
-\item 120 game tournament
-\item 120 game tournament
-\item 120 game tournament
+\item 120 Game tournament
+\item 120 Game tournament
+\item 120 Game tournament
 \end{itemize}
 
-This procedure was repeated twice to reach the total of 9 tournaments respectively. The machine-learning bots did not compete against eachother.
-Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.
+This procedure was repeated twice to reach the total of 9 tournaments respectively.
+The testing only occured between learning and non-learning bots.
+The learning bots did not compete against eachother.
+In case of Rand and Bully, the training process consisted of 100,000 observations of the (non-learning) opponent .
+Rdeep was only observed 10,000 times during training.
 

### 2018-01-31 Text/R/Bully.R
Added some plots and edited results file

@@ -1,0 +1,7 @@
+meanArray = c(0.78,0.68,0.80,0.82,0.79,0.88)
+
+#normal names:
+#names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
+names(meanArray) = c("minimal", "stripped","ml","advancedSimple","advanced","combined")
+
+barplot(meanArray,names.arg =names(meanArray),ylim = c(0.6,1.0),ylab = "Part of games won", xpd = FALSE,main = "Means of tournaments against Rand")

### 2018-01-31 Text/R/Bully.R
Added barplots for Rdeep,bully (incomplete) and rand. R source files present

@@ -1,7 +1,8 @@
-meanArray = c(0.78,0.68,0.80,0.82,0.79,0.88)
+meanArray = c(0.78,0.00000000,0.81,0.71,0.75,0.70)
+              
 
 #normal names:
 #names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
-names(meanArray) = c("minimal", "stripped","ml","advancedSimple","advanced","combined")
-
-barplot(meanArray,names.arg =names(meanArray),ylim = c(0.6,1.0),ylab = "Part of games won", xpd = FALSE,main = "Means of tournaments against Rand")
+names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")
+bot = c("Bully")
+barplot(meanArray,names.arg =names(meanArray),ylim = c(0.6,1.0),ylab = "Part of games won", xpd = FALSE,main = paste("Part of games won against ",bot))

### 2018-01-31 Text/R/Rand.R

@@ -2,6 +2,6 @@ meanArray = c(0.78,0.68,0.80,0.82,0.79,0.88)
 
 #normal names:
 #names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
-names(meanArray) = c("minimal", "stripped","ml","advancedSimple","advanced","combined")
-
-barplot(meanArray,names.arg =names(meanArray),ylim = c(0.6,1.0),ylab = "Part of games won", xpd = FALSE,main = "Means of tournaments against Rand")
+names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")
+bot = c("Rand")
+barplot(meanArray,names.arg =names(meanArray),ylim = c(0.6,1.0),ylab = "Part of games won", xpd = FALSE,main = paste("Part of games won against ",bot))

### 2018-01-31 Text/R/Rdeep.R

@@ -1,0 +1,7 @@
+meanArray = c(0.32,0.26,0.24,0.26,0.27,0.25)
+
+#normal names:
+#names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
+names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")
+bot = c("Rdeep")
+barplot(meanArray,names.arg =names(meanArray),ylim = c(0,0.4),ylab = "Part of games won", xpd = FALSE,main = paste("Part of games won against ",bot))

### 2018-01-31 Text/paper.tex
Added shit merge blablabjkshjdhfkjsd

@@
 For this paper, we will be focussing on weak AI in games, more specifically in the game of Schnapsen.
-In section 2 we will describe Schnapsen in more detail, alongside the bots used for the game.
+In section 2 we will describe Schnapsen and the Schnapsen framework in detail, alongside the bots already implemented.
 The research question will be described in section 3.
-In section 4, we will talk more about the experiment.
-...
+In section 4, we will talk more about the machine-learning bots, and the research setup.
+Consequently in section 5 we will describe the results of the experiment, and in section 6 we will elaborate on our findings.
+Finally, in section 7 we will draw our conclusion.
 
@@
 
-\section{Machine Learning Bots Feature Space}
-For the purpose of our research, we created 5 machine-learning bots accompanying the original machine-learning bot.
-Below, we will give an overview of the bots and the changes made.
-For the whole overview, refer to appendix A:
-
-\subsection{ ml\_stripped}
-This bot stripped-down version of the original ml-bot. Its feature space only contains the perspective, and the point count of both player 1 and player 2.
-
-\subsection{ml\_minimal}
-...
-
-\subsection{ml\_advancedSimple}
-This bot has a slightly extended feature space in comparison to the original ml-bot.
-The added features are player 1 and player 2 points are squared and cubed and added to the feature space.
-The same goes for the pending points, these are also squared and cubed, and added to the feature space, in order to get more of a difference in the data points.
-
-\subsection{ml\_advanced}
-This bot has a more extended feature space.
-Added are differences between points, differences between pending points, trump card ratio in the hand, high-ranking card ratio (10's or A's) in the hand, number of trump cards in phase 2, number of same suit cards as opponent's played card, and number of points currently in the hand $^2$.
-
-\subsection{ml\_combined} 
-The ml-combined bot combines, the advancedSimple and advanced ml-bot, creating a bot with all feature space extensions.
-
 \section{Experimental setup}
-
-To answer our research question, multiple Schnapsen tournaments were held. Each learning bot played multiple 120 game tournaments against each individual non-learning bot.
+For the purpose of our research, we created 5 machine-learning bots accompanying the original machine-learning bot, each competing in multiple 120 game Schnapsen tournaments against each individual non-learning bot.
+Below, we will give an overview of the bots and the changes made with respect to the default machine-learning bot.
+For the whole overview, refer to appendix A.
+After that, we will describe the testing procedure.
 
@@
 \begin{description}
-\item [ml\_minimal:] This bot has only the perspective and both players points as features.
+\item [ml\_minimal:] This bot has only the perspective and the point count of both player 1 and player 2 as features.
 
@@
 
-\item [ml\_enriched:]  This bot has all the features of ml bot. In addition to the \textit{default feature space} the following features were added to the feature space:
+\item [ml\_enriched:]  This bot has a slightly extended feature space in comparison to the original ml-bot. The following features were added to the feature space:
 \begin{itemize}
@@
 
-\item [ml\_advanced:] ml\_advanced  has the following features in addition to the \textit{default feature space}:
+\item [ml\_advanced:] 
+This bot has a more extended feature space in addition to the \textit{default feature space}. Added are: 
 \begin{itemize}
@@
 \end{itemize}
+
+\item[ml\_combined:] This bot has the most extended feature space. It combines the features of ml\_enriched and ml\_advanced.
 \end{description}
-
 \subsection{The testing procedure}
@@
 \section{Overview of machine-learning bots' feature spaces}
+\subsection{ml\_minimal}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\end{itemize}
 \subsection{ml\_stripped}
@@
 \item Player 2's point count
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
 \end{itemize}
-\subsection{ml\_minimal}
-\subsection{ml\_advancedSimple}
+\subsection{ml\_enriched}
 \begin{itemize}
@@
 
-\item Bot:
+\item MyBot implementation:
+It plays any available trump card first. If none is available it picks a random card.
+
+\begin{lstlisting}[language=bash]
+def get_move(self, state):
+        moves = state.moves()
+        return get_trump_card(moves,state)
+def get_trump_card(moves,state):
+    randomChoice = random.choice(moves)
+    counter = 0
+    if randomChoice == None:
+        print "NONE FOUND"
+    if moves == None:
+        print "None available"
+        return None
+    while True:
+        randomChoice = random.choice(moves)
+        counter +=1
+        if randomChoice == None:
+            print "NONE returned"
+            return randomChoice
+        try:
+            if util.get_suit(randomChoice[0]) 
+            == State.get_trump_suit(state):
+                #print "Playing trump card"
+                return randomChoice
+        except:
+            #print "KEY ERROR"
+            pass
+        if counter > 40 and not randomChoice == None:
+            #print "Playing normal card"
+            return randomChoice
+    return randomChoice
+\end{lstlisting}
+
+When no legal moves are to be made except the best trump card you have no legal moves when you  remove the trump card from the list of legal moves.
+In that case the python program expects a move but it gets a return type "None".
+That's why it raises an error.
+
+Output:
+\begin{lstlisting}[language=bash]
+Results:
+    bot <bots.rand.rand.Bot instance at 0x7fe73586fab8>: 25 wins
+    bot <bots.mybot.mybot.Bot instance at 0x7fe73587a440>: 45 wins
+\end{lstlisting}
 
@@
 - Insert pdf here - This heatmap means:
+If player 2 has a high non-move probability, this is better for player 1 if player 1 has a low-non move probability.
+Both players seem to have a good value if the non-move probability is around 0.4 - 0.6.
 
@@
 
-\item
+\item The added code:
+
+It creates one instance for each bot, minimax and alphabeta.
+Then in generates a state, and it does a few random moves.
+It measures the time to get the next move from both the minimax and alphabeta, then it compares the outcomes.
+If they are equal it will print "Agreed." else it will display the answers of both bots.
+This process is repeated a few times.
+Even though the code is right, the checking program does not behave correctly. That's why we do not have a valid output.
 
@@
 If the value is -1.0, the opponent has a definite win.
+
+We came up with, the ratio of trump cards in hand, it turned out to be a horrible heuristic.
+Holding on to your trumps seems to be a bad tactic.
+Therefore we tried ditching trumps as soon as possible, this lead to somewhat better results, but random was still a better bot in the end.
+
 \end{enumerate}
@@
 
+\item 6)The playing ace strategy work:
+
+\begin{lstlisting}[language=bash]
+kb.add_clause(A0)
+kb.add_clause(A5)
+kb.add_clause(A10)
+kb.add_clause(A15)
+
+#PLAY ACE STRATEGY
+kb.add_clause(~A0, PA0)
+kb.add_clause(~A5, PA5)
+kb.add_clause(~A10, PA10)
+kb.add_clause(~A15, PA15)
+kb.add_clause(~PA0, A0)
+kb.add_clause(~PA5, A5)
+kb.add_clause(~PA10, A10)
+kb.add_clause(~PA15, A15)
+\end{lstlisting}
+
+When adding: 
+\begin{lstlisting}[language=bash]
+kb.add_clause(~PA0)
+\end{lstlisting}
+The statisfiability with the KB fails, therefore we know PA0 is entailed by the KB
+
+\item We implemented the PlayCheap strategy:
+
+\item Game output
+
 \item 
-
 \end{enumerate}
@@
 
+\item We created three ml bots:
+\begin{itemize}
+\item The first one was trained on rdeep
+\item The second one was trained on rand
+\item The third one was trained on the second bot.
+\end{itemize}
+
+We played a tournament with 300 games in total. The results:
+\begin{lstlisting}[language=bash]
+    bot <bots.ml.ml.Bot instance at 0x10ad81ef0>: 92 wins
+    bot <bots.ml.ml.Bot instance at 0x10ad81f80>: 99 wins
+    bot <bots.ml.ml.Bot instance at 0x10b80cb00>: 109 wins
+\end{lstlisting}
+As you can see, bot 3 only performed a bit better than the other two, but there is no really significant difference between the bots.
+
+\item For added features, read this research paper. It's all about added features.
+
 \end{enumerate}

### 2018-01-31 Text/R/Bully.R
Updated Bully.r with the last piece of data and generated new plot

@@ -1,4 +1,4 @@
-meanArray = c(0.78,0.00000000,0.81,0.71,0.75,0.70)
+meanArray = c(0.78,0.78,0.81,0.71,0.75,0.70)
               
 
 #normal names:

### 2018-02-01 bots/alphabeta/alphabeta.py
Added alphabeta

@@ -1,0 +1,91 @@
+#!/usr/bin/env python
+"""
+
+
+"""
+
+from api import State, util
+import random
+
+class Bot:
+
+    __max_depth = -1
+    __randomize = True
+
+    def __init__(self, randomize=True, depth=6):
+        self.__randomize = randomize
+        self.__max_depth = depth
+
+    def get_move(self, state):
+        val, move = self.value(state)
+
+        return move # to do nothing, return None
+
+    def value(self, state, alpha=float('-inf'), beta=float('inf'), depth = 0):
+        """
+        Return the value of this state and the associated move
+        :param State state:
+        :param float alpha: The highest score that the maximizing player can guarantee given current knowledge
+        :param float beta: The lowest score that the minimizing player can guarantee given current knowledge
+        :param int depth: How deep we are in the tree
+        :return val, move: the value of the state, and the best move.
+        """
+        if state.finished():
+            return (1.0, None) if state.winner() == 1 else (-1.0, None)
+
+        if depth == self.__max_depth:
+            return heuristic(state)
+
+        best_value = float('-inf') if maximizing(state) else float('inf')
+        best_move = None
+
+        moves = state.moves()
+
+        if self.__randomize:
+            random.shuffle(moves)
+
+        for move in moves:
+
+            next_state = state.next(move)
+            value = self.value(next_state,alpha,beta,depth+1)[0]
+
+            if maximizing(state):
+                if value > best_value:
+                    best_value = value
+                    best_move = move
+                    alpha = best_value
+            else:
+                if value < best_value:
+                    best_value = value
+                    best_move = move
+                    beta = best_value
+
+            # Prune the search tree
+            # We know this state will never be chosen, so we stop evaluating its children
+            if maximizing(state):
+                if alpha > beta:
+                    break
+            else:
+                if beta < alpha:
+                    break
+
+        return best_value, best_move
+
+def maximizing(state):
+    """
+    Whether we're the maximizing player (1) or the minimizing player (2).
+
+    :param state:
+    :return:
+    """
+    return state.whose_turn() == 1
+
+def heuristic(state):
+    # type: (State) -> float
+    """
+    Estimate the value of this state: -1.0 is a certain win for player 2, 1.0 is a certain win for player 1
+
+    :param state:
+    :return: A heuristic evaluation for the given state (between -1.0 and 1.0)
+    """
+    return util.ratio_points(state, 1) * 2.0 - 1.0, None

### 2018-02-01 Text/paper.tex
added images to the results page

@@
 \usepackage{enumerate}
+\usepackage{graphicx} % Required for including images
+\usepackage[font=small,labelfont=bf]{caption}
 
@@
 \begin{abstract}
-Abstract paragraph with abstract shit about abstract things
+This paper examines the effect of extended and narrowed feature spaces on logistic regression machine learning bot.
+To illustrate this, 5 different machine learning bots were created: two bots with narrowed feature spaces, three bots with extended feature spaces.
+These bots were trained multiple times, and played multiple tournaments against multiple other bots.
+The results are..
 \end{abstract}
@@
 Artificial Intelligence is becoming a huge subject, and we see it appearing more and more in daily life: voice assistants on smartphones, self-driving Tesla's, AlphaGo defeating Go masters, and so on.
-...
-We can make a distinction between strong and weak AI [1]: \textit{weak AI} is focused on mastering problems in one limited area, whereas \textit{strong AI} is considered to be Artificial Intelligence with \textit{actual} intelligence, and even self-awareness.
-For this paper, we will be focussing on weak AI in games, more specifically in the game of Schnapsen.
-In section 2 we will describe Schnapsen and the Schnapsen framework in detail, alongside the bots already implemented.
+within the field, we can make a distinction between strong and weak AI [1]: \textit{weak AI} is focused on mastering problems in one limited area, whereas \textit{strong AI} is considered to be Artificial Intelligence with \textit{actual} intelligence, and even self-awareness.
+For this paper, we will concentrate on weak AI in the game of Schnapsen.
+The weak-AI in this game are machine-learning bots.
+In this paper, we will specifically focus on the feature spaces of these machine-learning bots, and how the differences in features affect performance of the bots.
+In section 2 we will describe Schnapsen and the Schnapsen framework in detail, alongside the non-AI bots that have already been implemented.
 The research question will be described in section 3.
-In section 4, we will talk more about the machine-learning bots, and the research setup.
+In section 4, we will talk about the machine-learning (AI) bots, and the research setup.
 Consequently in section 5 we will describe the results of the experiment, and in section 6 we will elaborate on our findings.
@@
 \subsection{Machine Learning Bots}
-For this paper, we will use machine learning bots with different sets of features to determine what the best features are.
+For this paper, we will use machine learning bots.
+These bots use a logistic regression algorithm to create the model.
+The model estimates to probability of a certain response based on on or more features.
+[2] The model can be retrieved by training the bot against another player.
+The bot will use the model when playing the actual games.
+For more information on our implementation of the machine learning bots, refer to section 4.
 
+\clearpage
 \section{Research Question}
-In our research, we want to find what feature set will improve the machine learning bot's performance the most in Schnapsen.
-There is already a machine learning bot present, which acts as a base line - with what we will call, the \textit{default feature space}- provided by the framework.
+In our research, we want to find \textit{what feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
+With improve the most, we mean as seen from the baseline.
+There is already a machine learning bot present, which will act as this base line.
+This bot has, what we will call the \textit{default feature space}- provided by the framework.
 \\
@@
 \noindent
-Our goal is to build multiple bots machine learning bots, both with extended feature spaces and narrower feature spaces, and see which bot will perform best.
-With \textit{performs best}, we mean which bot will have the most wins against the other bots (rdeep, bully, rand, minimax, kbbot).
-Our hypothesis is that the bots with an extended feature space will outperform the bots with a narrower feature space.
-The default machine-learning bot will probably lie somewhere in the middle of the bots in terms of performance.
+Our goal is to build multiple bots machine learning bots, both with extended feature spaces and narrower feature spaces, and see which bot will improve most in relation to the default machine-learning bot.
+Our hypothesis is that the bots with an extended feature space will have a better performance the bots with a narrower feature space, and that the extended feature space bots will perform better than the default bot, where the narrow feature space will perform worse.
+This is because the narrowing of the feature space can cause underfitting, where the model 'cannot capture the underlying structure of the data'[3] increasing the chance of making a wrong prediction.
+Consequently, extending the feature space can cause overfitting, where the model has more features than the data needs, which can also lead to making the wrong predictions.
 
+\clearpage
 \section{Experimental setup}
 For the purpose of our research, we created 5 machine-learning bots accompanying the original machine-learning bot, each competing in multiple 120 game Schnapsen tournaments against each individual non-learning bot.
+All bots were trained and tested in the same way.
 Below, we will give an overview of the bots and the changes made with respect to the default machine-learning bot.
@@
 \begin{description}
-\item [ml\_minimal:] This bot has only the perspective and the point count of both player 1 and player 2 as features.
+\item [ml\_minimal:] This bot has the smallest feature space of all: only the perspective and the point count of both player 1 and player 2 as features.
+We wanted to see if a bot can still perform well, even if it just has minimal amount of information about the game state.
 
-\item [ml\_stripped:] ml\_stripped has all the \textit{default feature space} except for both players pending points and trumpsuit id.
+\item [ml\_stripped:] ml\_stripped has almost all the features of the \textit{default feature space} except for both players pending points and trumpsuit id.
 
@@
 \end{itemize}
+These features were added to go more to a design-matrix like feature space. Since the amount of points a player has are important for the game, we chose to focus solely on this.
 
@@
 \end{itemize}
+This is the bot where we chose to add more of our own thought of features.
+Point difference was added, since this is a good indicator if a player is leading the game by a high margin.
+Furthermore, we chose to focus on both trump and high-ranking cards in the hand.
+The more you have, the better it is.
+The number of trump cards in phase 2 is also important: If you still got all your trump cards in phase 2 of the game, you have a high chance of beating your opponent.
+Furthermore the number of cards with same suit as opponents played suit feature was added, alongside the number of points in the player hand squared feature.
 
@@
 This procedure was repeated twice to reach the total of 9 tournaments respectively.
-The testing only occured between learning and non-learning bots.
-The learning bots did not compete against eachother.
-In case of Rand and Bully, the training process consisted of 100,000 observations of the (non-learning) opponent .
-Rdeep was only observed 10,000 times during training.
+The testing only occurred between learning and non-learning bots.
+The learning bots did not compete against each other.
+In case of Rand and Bully, each training process consisted of 100,000 observations of the (non-learning) opponent.
+Rdeep was only observed 10,000 times during training, since training this bot takes a substantial amount of time.
+\clearpage
+\section{Results}
+The tournament results are presented in Table 1.
 
-\section{Results}
+\begin{center}
+  \begin{tabular}{ | l | l l | l l | l l | | l l | }
+     \hline
+      & \textbf{rand} & & \textbf{bully} & & \textbf{rdeep} & & \textbf{Total} & \\
+      & wins & losses & wins & losses & wins & losses  & wins & losses\\ \hline
+      ml\_minimal & 843 & 237 & 837 & 243 & 348 & 732 & 2028 & 1212 \\ \hline
+      ml\_stripped & 736 & 344 & 843 & 237 & 283 & 797 & 1862 & 1378  \\ \hline
+      ml & 866 & 214 & 876 & 204 & 257 & 823 & 1999 & 1241 \\ \hline
+      ml\_enriched & 881 & 119 & 797 & 283 & 284 & 798 & 1962 & 1278 \\ \hline
+      ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
+      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806 & 1982 & 1258 \\ \hline
+  \end{tabular}
+\end{center}
+
+\textbf{Table 1}: Overview of tournament wins and losses per ml-bot. \\
+
+\begin{center}
+\begin{tabular}{| r | r | r | r || r |}
+\hline
+      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
+      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
+      ml\_stripped & -15\% & -3,76\% & 10,11\% & \textbf{-6,85\%}  \\ \hline
+      ml\_enriched & +1,73\% & -9,01\% & 10,5\% & \textbf{- 1,85\%} \\ \hline
+      ml\_advanced & -1,15\% & -7,76\% & 13,6\%& \textbf{-2,15\%}  \\ \hline
+      ml\_combined & 9,58\% & -13,35\% & 6,61\% & \textbf{-0,85\%}  \\ \hline \hline
+      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{15,24\%} & \textbf{-2,05\%} \\ \hline
+\end{tabular} \\
+\end{center}
+
+\textbf{Table 2}: Improvement over ml. \\
+
+\begin{center}
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\linewidth]{images/barplotRand.png}
+\captionof{figure}{Part of games won against Rand}
+\end{minipage}
+\hfill
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\linewidth]{images/barplotBully.png}
+\captionof{figure}{Part of games won against Bully}
+\end{minipage}
+      \\ %extra line for space
+\begin{minipage}{0.5\linewidth}
+\includegraphics[width=\linewidth]{images/barplotRdeep.png}
+\captionof{figure}{Part of games won against Rdeep (notice the Y-axis)}
+\end{minipage}
+\end{center}
+
+The collected data .............
 
@@
 1. http://humanparagon.com/strong-and-weak-ai/
+2. https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f
+3. https://en.wikipedia.org/wiki/Overfitting
 
-appendix
+Appendix
 \section{Overview of machine-learning bots' feature spaces}

### 2018-02-01 Text/paper.tex
added table + and -, and started with findings

@@
 \usepackage[font=small,labelfont=bf]{caption}
+\usepackage{geometry}
 
@@
 
+\setlength{\leftmargin}{0pt}
 \begin{center}
-  \begin{tabular}{ | l | l l | l l | l l | | l l | }
+  \begin{tabular}{ | l | l l | l l | l l | |l l | }
      \hline
       & \textbf{rand} & & \textbf{bully} & & \textbf{rdeep} & & \textbf{Total} & \\
-      & wins & losses & wins & losses & wins & losses  & wins & losses\\ \hline
+      & wins & losses & wins & losses & wins & losses  & wins & losses \\ \hline
       ml\_minimal & 843 & 237 & 837 & 243 & 348 & 732 & 2028 & 1212 \\ \hline
@@
       ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
-      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806 & 1982 & 1258 \\ \hline
+      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806  & 1982 & 1258\\ \hline
   \end{tabular}
 \end{center}
-
 \textbf{Table 1}: Overview of tournament wins and losses per ml-bot. \\
@@
       ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
-      ml\_stripped & -15\% & -3,76\% & 10,11\% & \textbf{-6,85\%}  \\ \hline
-      ml\_enriched & +1,73\% & -9,01\% & 10,5\% & \textbf{- 1,85\%} \\ \hline
-      ml\_advanced & -1,15\% & -7,76\% & 13,6\%& \textbf{-2,15\%}  \\ \hline
-      ml\_combined & 9,58\% & -13,35\% & 6,61\% & \textbf{-0,85\%}  \\ \hline \hline
-      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{15,24\%} & \textbf{-2,05\%} \\ \hline
+      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
+      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
+      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
+      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
+      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
 \end{tabular} \\
@@
       \\ %extra line for space
-\begin{minipage}{0.5\linewidth}
+\begin{minipage}{0.49\linewidth}
 \includegraphics[width=\linewidth]{images/barplotRdeep.png}
@@
 
-The collected data .............
+\section{Findings}
+From the collected data we have x conclusions.
 
-\section{Findings}
+\subsection*{Against Rand}
+
+\subsection*{Against Bully}
+
+\subsection*{Against Rdeep}
+First of all, the learning bots performed worse than rdeep.The worst performer was, surprisingly, the stock ml bot. The performance of each bot
 

### 2018-02-01 train-ml-bot.py

@@ -17,21 +17,24 @@ from sklearn.externals import joblib
 from bots.rand import rand
 from bots.rdeep import rdeep
 from bots.bully import bully
+from bots.alphabeta import alphabeta
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
+
 
 #Pick the features of which bot you want to use for training the model:
 from bots.ml.ml import features
 #from bots.ml_advanced.ml_advanced import features
 # How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
+player = alphabeta.Bot()
 #player = rand.Bot()
-player = rdeep.Bot()
+#player = rdeep.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-02-01 train-ml_advanced-bot.py

@@ -19,20 +19,18 @@ from bots.rdeep import rdeep
 from bots.bully import bully
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
+from bots.alphabeta import alphabeta
 
 #Pick the features of which bot you want to use for training the model:
 from bots.ml.ml import features
 from bots.ml_advanced.ml_advanced import features
-# How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
-#player = rand.Bot()
-#player = rdeep.Bot()
-player = bully.Bot()
+player = alphabeta.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-02-01 train-ml_combined-bot.py

@@ -19,18 +19,17 @@ from bots.rdeep import rdeep
 from bots.bully import bully
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
-
+from bots.alphabeta import alphabeta
 #Pick the features of which bot you want to use for training the model:
 from bots.ml_combined.ml_combined import features
 #from bots.ml_advanced.ml_advanced import features
-# How many games to play
 GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
-player = rand.Bot()
+player = alphabeta.Bot()
 #player = rdeep.Bot()
 #player = ml_advanced.Bot()
 

### 2018-02-01 train-ml_lucas-bot.py

@@ -19,19 +19,18 @@ from bots.rdeep import rdeep
 from bots.bully import bully
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
+from bots.alphabeta import alphabeta
 
 #Pick the features of which bot you want to use for training the model:
 #from bots.ml.ml import features
 from bots.ml_lucas.ml_lucas import features
-# How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
-#player = rand.Bot()
-player = rdeep.Bot()
+player = alphabeta.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-02-01 train-ml_minimal-bot.py

@@ -19,20 +19,18 @@ from bots.rdeep import rdeep
 from bots.bully import bully
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
+from bots.alphabeta import alphabeta
 
 #Pick the features of which bot you want to use for training the model:
 #from bots.ml.ml import features
 from bots.ml_minimal.ml_minimal import features
-# How many games to play
-GAMES = 10000
+GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
-#player = rand.Bot()
-#player = rdeep.Bot()
-player = bully.Bot()
+player = alphabeta.Bot()
 #player = ml_advanced.Bot()
 
 data = []

### 2018-02-01 train-ml_stripped-bot.py

@@ -19,18 +19,18 @@ from bots.rdeep import rdeep
 from bots.bully import bully
 from bots.ml_advanced import ml_advanced
 from bots.ml import ml
+from bots.alphabeta import alphabeta
 
 #Pick the features of which bot you want to use for training the model:
 #from bots.ml.ml import features
 from bots.ml_stripped.ml_stripped import features
-# How many games to play
 GAMES = 100000
 
 # Which phase the game starts in
-PHASE = 1
+PHASE = 2
 
 # The player we'll observe
-player = rand.Bot()
+player = alphabeta.Bot()
 #player = rdeep.Bot()
 #player = ml_advanced.Bot()
 

### 2018-02-01 Text/paper.tex
added standard deviations (of all the means) to the findings

@@
 \includegraphics[width=\linewidth]{images/barplotRdeep.png}
-\captionof{figure}{Part of games won against Rdeep (notice the Y-axis)}
+\captionof{figure}{Part of games won against Rdeep (please notice the Y-axis)}
 \end{minipage}
@@
 \subsection*{Against Rand}
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314
 
 \subsection*{Against Bully}
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against bully is 0.0432435
 
 \subsection*{Against Rdeep}
-First of all, the learning bots performed worse than rdeep.The worst performer was, surprisingly, the stock ml bot. The performance of each bot
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758.
+First of all, the learning bots performed worse than rdeep.
+The worst performer was, surprisingly, the stock ml bot.
+However, the results of the bots are relatively close, except for the ml\_minimal bot.
 

### 2018-02-01 Text/R/Bully.R

@@ -1,6 +1,6 @@
 meanArray = c(0.78,0.78,0.81,0.71,0.75,0.70)
               
-
+sd(meanArray)
 #normal names:
 #names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
 names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")

### 2018-02-01 Text/R/Rand.R

@@ -1,5 +1,5 @@
 meanArray = c(0.78,0.68,0.80,0.82,0.79,0.88)
-
+sd(meanArray)
 #normal names:
 #names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
 names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")

### 2018-02-01 Text/R/Rdeep.R

@@ -1,5 +1,5 @@
 meanArray = c(0.32,0.26,0.24,0.26,0.27,0.25)
-
+sd(meanArray)
 #normal names:
 #names(meanArray) = c("ml_minimal", "ml_stripped","ml","ml_advancedSimple","ml_advanced","ml_combined")
 names(meanArray) = c("minimal", "stripped","ml","enriched","advanced","combined")

### 2018-02-01 Text/paper.tex
added rand findings
wrote a little section on rand findings, not sure where to put standard deviation yet.

@@
 \subsection*{Against Rand}
-The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314. 
+There are a few notable things when comparing the performance of our bots.
+Firstly, while both ml\_minimal and ml\_stripped performed worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal, despite the latter of the two having the smaller feature set.
+Secondly, stripping away most of the feature set in ml\_minimal only led to a relatively small performance loss.
+Lastly, while ml\_enriched and ml\_advanced perform, respectively, a little better and a little worse when compared to the stock ml bot, when we combined the feature sets of these two bots in ml\_combined, it led to an performance increase of almost 10\% compared to the default ml bot.
 

### 2018-02-01 Text/paper.tex
Added a little bit of information to findings/rdeep

--- 2018-02-01 Text/paper.tex
@@
 The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758.
-First of all, the learning bots performed worse than rdeep.
+This number is the lowest of all the non-learning bots and is clearly confirmed by the barplot in figure 3.
+Rdeep won the majority of the games, which results in a low diversity of winning scores among the learning bots.
 The worst performer was, surprisingly, the stock ml bot.
-However, the results of the bots are relatively close, except for the ml\_minimal bot.
+The only bot  results of the bots are relatively close, except for the ml\_minimal bot.
+WIP
 

### 2018-02-01 Text/paper.tex
Added rdeep bot and edited a part of rand in findings

--- 2018-02-01 Text/paper.tex
@@
 \textbf{Table 2}: Improvement over ml. \\
+\begin{center}
+\begin{tabular}{| r | r | r | r |}
+\hline
+      & \textbf{rand} & \textbf{bully} & \textbf{rdeep}\\ \hline
+      Standard deviation & 0.0652 & 0.0432 & 0.0280    \\ \hline
+\end{tabular} \\
+\end{center}
+
+\textbf{Table 3}: \textit{Standard deviation} of the mean of the 9 tournaments for each bot. \\
 
@@
 \section{Findings}
-From the collected data we have x conclusions.
 
 \subsection*{Against Rand}
-The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314
+There are a few notable things when comparing the performance of our bots.
+Firstly, while both ml\_minimal and ml\_stripped performed worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal.
+Despite the latter of the two having the smallest feature set.
+Secondly, stripping away most of the feature set in ml\_minimal only led to a relatively small performance loss.
+Lastly, ml\_enriched and ml\_advanced perform, respectively, a little better and a little worse when compared to the stock ml bot.
+However, when we combined the feature sets of these two bots in ml\_combined, it led to an performance increase of almost 10\% compared to the stock ml bot.
+In short, the bots with the larger feature spaces did perform relatively better against rand.
 
 \subsection*{Against Bully}
-The \textit{standard deviation} of the mean of the 9 tournaments for each bot against bully is 0.0432435
 
 \subsection*{Against Rdeep}
-The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758.
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.0280.
 This number is the lowest of all the non-learning bots and is clearly confirmed by the barplot in figure 3.
@@
 The worst performer was, surprisingly, the stock ml bot.
-The only bot  results of the bots are relatively close, except for the ml\_minimal bot.
-WIP
+Although the variance in the winning scores is low, the ml\_minimal bot performs clearly better against rdeep.
+Compared to the other learning bots, ml\_minimal performs approximately 25\% better.
+Remarkable is the low score of ml\_combined with the most features of all.
+The other bots containing a larger feature space did perform slightly better than the stock ml bot.
+However, the bots with the smallest featurespaces seemed to perform the best against rdeep.
 
 \section{Conclusion}
+Performance is different per bot, and we can not say a lot since we do not have the data to do so , not enough data blabalablalbalalb
 

### 2018-02-01 Text/paper.tex
fixed table1  Bully ml_enriched entry and WIP Bully findings

@@
 Rdeep was only observed 10,000 times during training, since training this bot takes a substantial amount of time.
+The margin of error we adhere is 5\%.
 \clearpage
@@
       ml & 866 & 214 & 876 & 204 & 257 & 823 & 1999 & 1241 \\ \hline 
-      ml\_enriched & 881 & 119 & 797 & 283 & 284 & 798 & 1962 & 1278 \\ \hline
+      ml\_enriched & 881 & 119 & 772 & 308 & 284 & 798 & 1937 & 1303 \\ \hline
       ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
@@
 There are a few notable things when comparing the performance of our bots.
-Firstly, while both ml\_minimal and ml\_stripped performed worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal.
+Firstly, while both ml\_minimal and ml\_stripped performed slightly worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal.
 Despite the latter of the two having the smallest feature set.
+However, the differences are below 5\% and therefore within the margin of error.
 Secondly, stripping away most of the feature set in ml\_minimal only led to a relatively small performance loss.
@@
 \subsection*{Against Bully}
+
+Notable for the results of the bots against the bully bot are the following points.
+First of all, the stock ml bot performed the best of all bots.
+In figure 2 this is clearly noticable.
+Secondly,  the bots with larger feature spaces than the ml bot peformed significantly worse.
+Especially ml\_combined and ml
 
@@
 Compared to the other learning bots, ml\_minimal performs approximately 25\% better.
-Remarkable is the low score of ml\_combined with the most features of all.
-The other bots containing a larger feature space did perform slightly better than the stock ml bot.
-However, the bots with the smallest featurespaces seemed to perform the best against rdeep.
+Also remarkable is the relatively low score of ml\_combined with the most features of all.
+The other bots containing a larger feature space did perform slightly better than the stock ml bot, although this is all within the margin of error.
+Summarized, the bots with the smallest featurespaces seemed to perform the best against rdeep.
 

### 2018-02-01 Text/paper.tex
Changed things

@@
       ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
-      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
+      ml\_enriched & +1,73\% & -11,87\% & +10,5\% & \textbf{-3,10\%} \\ \hline
       ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
       ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
-      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
+      Average improvement & \textbf{-1,5\%} & \textbf{-8,24\%} & \textbf{+15,24\%} &\textbf{-2,3\%} \\ \hline
 \end{tabular} \\
@@
 
-\item Game output
+\begin{lstlisting}[language=bash]
+from kb import KB, Boolean, Integer
 
-\item 
+# Initialise all variables that you need for you strategies and game knowledge.
+# Add those variables here.. The following list is complete for the Play Jack strategy.
+J0 = Boolean('j0')
+J1 = Boolean('j1')
+J2 = Boolean('j2')
+J3 = Boolean('j3')
+J4 = Boolean('j4')
+J5 = Boolean('j5')
+J6 = Boolean('j6')
+J7 = Boolean('j7')
+J8 = Boolean('j8')
+J9 = Boolean('j9')
+J10 = Boolean('j10')
+J11 = Boolean('j11')
+J12 = Boolean('j12')
+J13 = Boolean('j13')
+J14 = Boolean('j14')
+J15 = Boolean('j15')
+J16 = Boolean('j16')
+J17 = Boolean('j17')
+J18 = Boolean('j18')
+J19 = Boolean('j19')
+PJ0 = Boolean('pj0')
+
+Q0 = Boolean('q0')
+Q1 = Boolean('q1')
+Q2 = Boolean('q2')
+Q3 = Boolean('q3')
+Q4 = Boolean('q4')
+Q5 = Boolean('q5')
+Q6 = Boolean('q6')
+Q7 = Boolean('q7')
+Q8 = Boolean('q8')
+Q9 = Boolean('q9')
+Q10 = Boolean('q10')
+Q11 = Boolean('q11')
+Q12 = Boolean('q12')
+Q13 = Boolean('q13')
+Q14 = Boolean('q14')
+Q15 = Boolean('q15')
+Q16 = Boolean('q16')
+Q17 = Boolean('q17')
+Q18 = Boolean('q18')
+Q19 = Boolean('q19')
+
+K0 = Boolean('k0')
+K1 = Boolean('k1')
+K2 = Boolean('k2')
+K3 = Boolean('k3')
+K4 = Boolean('k4')
+K5 = Boolean('k5')
+K6 = Boolean('k6')
+K7 = Boolean('k7')
+K8 = Boolean('k8')
+K9 = Boolean('k9')
+K10 = Boolean('k10')
+K11 = Boolean('k11')
+K12 = Boolean('k12')
+K13 = Boolean('k13')
+K14 = Boolean('k14')
+K15 = Boolean('k15')
+K16 = Boolean('k16')
+K17 = Boolean('k17')
+K18 = Boolean('k18')
+K19 = Boolean('k19')
+
+PC0 = Boolean('pc0')
+PC1 = Boolean('pc1')
+PC2 = Boolean('pc2')
+PC3 = Boolean('pc3')
+PC4 = Boolean('pc4')
+PC5 = Boolean('pc5')
+PC6 = Boolean('pc6')
+PC7 = Boolean('pc7')
+PC8 = Boolean('pc8')
+PC9 = Boolean('pc9')
+PC10 = Boolean('pc10')
+PC11 = Boolean('pc11')
+PC12 = Boolean('pc12')
+PC13 = Boolean('pc13')
+PC14 = Boolean('pc14')
+PC15 = Boolean('pc15')
+PC16 = Boolean('pc16')
+PC17 = Boolean('pc17')
+PC18 = Boolean('pc18')
+PC19 = Boolean('pc19')
+
+def general_information(kb):
+    # GENERAL INFORMATION ABOUT THE CARDS
+    # This adds information which cards are Jacks
+    kb.add_clause(J4)
+    kb.add_clause(~Q4)
+    kb.add_clause(~K4)
+    kb.add_clause(J9)
+    kb.add_clause(~Q9)
+    kb.add_clause(~K9)
+    kb.add_clause(J14)
+    kb.add_clause(~Q14)
+    kb.add_clause(~K14)
+    kb.add_clause(J19)
+    kb.add_clause(~Q19)
+    kb.add_clause(~K19)
+    kb.add_clause(Q3)
+    kb.add_clause(~K3)
+    kb.add_clause(~J3)
+    kb.add_clause(Q8)
+    kb.add_clause(~K8)
+    kb.add_clause(~J8)
+    kb.add_clause(Q13)
+    kb.add_clause(~K13)
+    kb.add_clause(~J13)
+    kb.add_clause(Q18)
+    kb.add_clause(~K18)
+    kb.add_clause(~J18)
+    kb.add_clause(K2)
+    kb.add_clause(~Q2)
+    kb.add_clause(~J2)
+    kb.add_clause(K7)
+    kb.add_clause(~Q7)
+    kb.add_clause(~J7)
+    kb.add_clause(K12)
+    kb.add_clause(~Q12)
+    kb.add_clause(~J12)
+    kb.add_clause(K17)
+    kb.add_clause(~Q17)
+    kb.add_clause(~J17)
+    # Add here whatever is needed for your strategy.
+
+def strategy_knowledge(kb):
+    # DEFINITION OF THE STRATEGY
+    # Add clauses (This list is sufficient for this strategy)
+    # PJ is the strategy to play jacks first, so all we need to model is all x PJ(x) <-> J(x),
+    # In other words that the PJ strategy should play a card when it is a jack
+    kb.add_clause(~PC4, J4, Q4, K4)
+    kb.add_clause(~PC9, J9, Q9, K9)
+    kb.add_clause(~PC14, J14, Q14, K14)
+    kb.add_clause(~PC19, J14, Q14, K14)
+
+    kb.add_clause(PC4, ~J4, ~Q4, ~K4)
+    kb.add_clause(PC9, ~J9, ~Q9, ~K9)
+    kb.add_clause(PC14, ~J14, ~Q14, ~K14)
+    kb.add_clause(PC19, ~J14, ~Q14, ~K14)
+
+    kb.add_clause(~PC3, J3, Q3, K3)
+    kb.add_clause(~PC8, J8, Q8, K8)
+    kb.add_clause(~PC13, J13, Q13, K13)
+    kb.add_clause(~PC18, J18, Q18, K18)
+
+    kb.add_clause(PC3, ~J3, ~Q3, ~K3)
+    kb.add_clause(PC8, ~J3, ~Q3, ~K3)
+    kb.add_clause(PC13, ~J13, ~Q13, ~K13)
+    kb.add_clause(PC18, ~J18, ~Q18, ~K18)
+
+    kb.add_clause(~PC2, J2, Q2, K2)
+    kb.add_clause(~PC7, J7, Q7, K7)
+    kb.add_clause(~PC12, J12, Q12, K12)
+    kb.add_clause(~PC17, J17, Q17, K17)
+
+    kb.add_clause(PC2, ~J2, ~Q2, ~K2)
+    kb.add_clause(PC7, ~J7, ~Q7, ~K7)
+    kb.add_clause(PC12, ~J12, ~Q12, ~K12)
+    kb.add_clause(PC17, ~J17, ~Q17, ~K17)
+
+8. Game output:
+   Start state: The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: C
+Player 1's hand: AC KD QD QS JS
+Player 2's hand: 10C QC JC 10H JH
+There are 10 cards in the stock
+
+player1: <bots.kbbot.kbbot.Bot instance at 0x102a72290>
+player2: <bots.rand.rand.Bot instance at 0x102a72518>
+*   Player 2 plays: JC
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: C
+Player 1's hand: AC KD QD QS JS
+Player 2's hand: 10C QC JC 10H JH
+There are 10 cards in the stock
+Player 2 has played card: J of C
+
+*   Player 1 plays: JS
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 4, pending: 0
+The trump suit is: C
+Player 1's hand: AC KD QD AS QS
+Player 2's hand: 10C QC 10H QH JH
+There are 8 cards in the stock
+
+*   Player 2 plays: QH
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 4, pending: 0
+The trump suit is: C
+Player 1's hand: AC KD QD AS QS
+Player 2's hand: 10C QC 10H QH JH
+There are 8 cards in the stock
+Player 2 has played card: Q of H
+
+*   Player 1 plays: KD
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 11, pending: 0
+The trump suit is: C
+Player 1's hand: AC QD KH AS QS
+Player 2's hand: 10C QC 10H JH 10S
+There are 6 cards in the stock
+
+*   Player 2 plays: JH
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 11, pending: 0
+The trump suit is: C
+Player 1's hand: AC QD KH AS QS
+Player 2's hand: 10C QC 10H JH 10S
+There are 6 cards in the stock
+Player 2 has played card: J of H
+
+*   Player 1 plays: AS
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 24, pending: 0
+The trump suit is: C
+Player 1's hand: AC QD KH KS QS
+Player 2's hand: 10C QC JD 10H 10S
+There are 4 cards in the stock
+
+*   Player 2 plays: QC
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 24, pending: 0
+The trump suit is: C
+Player 1's hand: AC QD KH KS QS
+Player 2's hand: 10C QC JD 10H 10S
+There are 4 cards in the stock
+Player 2 has played card: Q of C
+
+*   Player 1 plays: QD
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 30, pending: 0
+The trump suit is: C
+Player 1's hand: AC 10D KH KS QS
+Player 2's hand: 10C AD JD 10H 10S
+There are 2 cards in the stock
+
+*   Player 2 plays: 10C
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 30, pending: 0
+The trump suit is: C
+Player 1's hand: AC 10D KH KS QS
+Player 2's hand: 10C AD JD 10H 10S
+There are 2 cards in the stock
+Player 2 has played card: 10 of C
+
+*   Player 1 plays: KH
+The game is in phase: 2
+Player 1's points: 0, pending: 0
+Player 2's points: 44, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC 10D KS QS
+Player 2's hand: AD JD AH 10H 10S
+There are 0 cards in the stock
+
+*   Player 2 plays: 10S
+The game is in phase: 2
+Player 1's points: 0, pending: 0
+Player 2's points: 44, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC 10D KS QS
+Player 2's hand: AD JD AH 10H 10S
+There are 0 cards in the stock
+Player 2 has played card: 10 of S
+
+*   Player 1 plays: QS
+The game is in phase: 2
+Player 1's points: 0, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC 10D KS
+Player 2's hand: AD JD AH 10H
+There are 0 cards in the stock
+
+*   Player 2 plays: JD
+The game is in phase: 2
+Player 1's points: 0, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC 10D KS
+Player 2's hand: AD JD AH 10H
+There are 0 cards in the stock
+Player 2 has played card: J of D
+
+*   Player 1 plays: 10D
+The game is in phase: 2
+Player 1's points: 12, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC KS
+Player 2's hand: AD AH 10H
+There are 0 cards in the stock
+
+*   Player 1 plays: KS
+The game is in phase: 2
+Player 1's points: 12, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC KS
+Player 2's hand: AD AH 10H
+There are 0 cards in the stock
+Player 1 has played card: K of S
+
+*   Player 2 plays: AD
+The game is in phase: 2
+Player 1's points: 27, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC
+Player 2's hand: AH 10H
+There are 0 cards in the stock
+
+*   Player 1 plays: AC
+The game is in phase: 2
+Player 1's points: 27, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: AC KC
+Player 2's hand: AH 10H
+There are 0 cards in the stock
+Player 1 has played card: A of C
+
+*   Player 2 plays: AH
+The game is in phase: 2
+Player 1's points: 49, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: KC
+Player 2's hand: 10H
+There are 0 cards in the stock
+
+*   Player 1 plays: KC
+The game is in phase: 2
+Player 1's points: 49, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand: KC
+Player 2's hand: 10H
+There are 0 cards in the stock
+Player 1 has played card: K of C
+
+*   Player 2 plays: 10H
+The game is in phase: 2
+Player 1's points: 66, pending: 0
+Player 2's points: 57, pending: 0
+The trump suit is: C
+Player 1's hand:
+Player 2's hand:
+There are 0 cards in the stock
+
+Game finished. Player 1 has won, receiving 1 points.
+\end{lstlisting}
 \end{enumerate}

### 2018-02-01 Text/paper.tex
findings updated

--- 2018-02-01 Text/paper.tex
@@
 
-Notable for the results of the bots against the bully bot are the following points.
+Notable for the results of the tournaments against the bully bot are the following points.
 First of all, the stock ml bot performed the best of all bots.
 In figure 2 this is clearly noticable.
-Secondly,  the bots with larger feature spaces than the ml bot peformed significantly worse.
-Especially ml\_combined and ml
+Secondly,  ml\_stripped and ml\_minimal peformed comparable to ml bot.
+Therefore, we may conclude the smaller feature spaces do not cause a heavy impact on the performance of a learning bot.
+The last and most remarkable finding is the peformance of the ml\_enriched and ml\_combined bots.
+All bots with larger feature spaces peformed worse than ml bot.
+However, ml\_enriched and ml\_combined performed the worst with a performance decrease of approximately 9\%.
 
@@
 
-Appendix
-\section{Overview of machine-learning bots' feature spaces}
+\clearpage
+\section{Appendix}
+\subsection{Overview of machine-learning bots' feature spaces}
 \subsection{ml\_minimal}

### 2018-02-01 Text/paper.tex

--- 2018-02-01 Text/paper.tex
@@
+<<<<<<< HEAD
+\documentclass[a4paper,11pt]{article}
+
+\usepackage{listings}
+\usepackage{enumerate}
+\usepackage{graphicx} % Required for including images
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage{geometry}
+
+\title{The benefits of an extended feature space in a machine learning bot for the game Schnapsen}
+\date{January 25, 2018}
+\author{Lucas Faijdherbe, Daan Schrage and Ruben van der Ham\\\\
+	\small Intelligent Systems\\
+	\small Vrije Universiteit Amsterdam}
+
+\begin{document}
+\maketitle
+\clearpage
+
+\begin{abstract}
+This paper examines the effect of extended and narrowed feature spaces on logistic regression machine learning bot.
+To illustrate this, 5 different machine learning bots were created: two bots with narrowed feature spaces, three bots with extended feature spaces.
+These bots were trained multiple times, and played multiple tournaments against multiple other bots.
+The results are..
+\end{abstract}
+
+\section{Introduction}
+Artificial Intelligence is becoming a huge subject, and we see it appearing more and more in daily life: voice assistants on smartphones, self-driving Tesla's, AlphaGo defeating Go masters, and so on.
+within the field, we can make a distinction between strong and weak AI [1]: \textit{weak AI} is focused on mastering problems in one limited area, whereas \textit{strong AI} is considered to be Artificial Intelligence with \textit{actual} intelligence, and even self-awareness.
+For this paper, we will concentrate on weak AI in the game of Schnapsen.
+The weak-AI in this game are machine-learning bots.
+In this paper, we will specifically focus on the feature spaces of these machine-learning bots, and how the differences in features affect performance of the bots.
+In section 2 we will describe Schnapsen and the Schnapsen framework in detail, alongside the non-AI bots that have already been implemented.
+The research question will be described in section 3.
+In section 4, we will talk about the machine-learning (AI) bots, and the research setup.
+Consequently in section 5 we will describe the results of the experiment, and in section 6 we will elaborate on our findings.
+Finally, in section 7 we will draw our conclusion.
+
+\section{Background Information}
+\subsection{Schnapsen}
+Schnapsen is an Austrian card game, played with 20 cards; Only the Jacks, Queens, Kings, 10s and Aces are in the deck.
+The goal of the game is to win tricks, and to be the first player to score 66 points.
+Each game has a trump suit, which is determined randomly.
+A card from the trump suit lets you automatically win the trick, provided that there is no higher trump card in the game.
+
+The game has a multi-agent (we have an opponent), deterministic (the environment is determined by the current state and executed action), static (the environment does not change when an agent is choosing an action) and discrete (the game is turn-based) environment.
+The game consists of two phases: In phase one, when there are still cards in stock, we have an imperfect information game.
+In phase two, when the stock is depleted, we have a perfect information game, since we know exactly what the cards of our opponent are.
+The point count in the game is as follows: \\ \\
+\noindent
+\begin{tabular}{l l l l l}
+\textbf{J} & \textbf{Q} & \textbf{K} & \textbf{10} & \textbf{A} \\
+2 & 3 & 4 & 10 & 11 \\
+\end{tabular} \\
+
+\noindent
+A lot of points can also be won by marriages.
+If the player is leading the trick and has a king or a queen of the same suit, it can play one card, and show the other, so the opponent knows that there is a marriage.\\ \\
+\noindent
+\begin{tabular} {c c}
+\textbf{Normal marriage (non-trump suit)} & \textbf{Royal marriage (trump suit)} \\
+20 & 40 \\
+\end{tabular}\\
+
+\noindent
+The game starts in phase one, an imperfect-information game.
+Each agent has 5 cards.
+Player 1 plays a card, thereby determining the suit that has to be played.
+To win the trick, player 2 has to play a higher-ranking card from the same suit, or a trump card.
+Player 2 does not have to follow suit in phase 1, but he/she will lose the trick in that case.
+The winner of the trick now becomes player one and gets the cards, with the amount of points the two cards represent.
+This goes on until the stock is depleted; then we enter phase 2, a perfect-information game.
+Player 2 now has to follow suit.
+If it cannot do that, the player has to trump, and otherwise play any card.
+If a player reaches 66 points or more, the game is over.
+
+\subsection{Intelligent Systems Schnapsen Framework}
+An API in Python has been provided, together with a framework for the Schnapsen game.
+Furthermore, we  have two scripts: one where bots can play against each other in a single game where all moves in the game can be seen, and a script where bots play a tournament against each other - with a specifiable number of games to be played - and where the number of won games per robot can be seen.
+There are already multiple bots present in the framework to play against:
+\begin{description}
+\item [Minimax / Alphabeta:] This bot only works in a perfect-information game (phase 2 of Schnapsen).
+It recursively looks through all the states, and decides what the best move to play will be, provided that the opponent plays optimally, and will try to minimize the outcome of the game for the player.
+\item [Bully:] Plays by a defined set of rules.
+If it has a trump card, it will play that.
+Otherwise, it will play a card of the same suit player 1 played.
+If it cannot do either of those things, it will play the highest ranking card of any suit.
+\item [Rand:] Chooses a random move out of all of the legal moves, and plays that.
+\item [Rdeep:] Functions quite like a Monte-Carlo sampling bot.
+It looks through multiple states, and averages the heuristics of a state, thereby ranking the moves.
+It then picks one of the highest ranking moves to play.
+\item [KBbot:] Logical reasoning bot. The strategy can be defined in propositional logic. The current strategy of the bot is to always play cheap cards (i.e kings, queens, jacks) first.
+\end{description}
+
+\subsection{Machine Learning Bots}
+For this paper, we will use machine learning bots.
+These bots use a logistic regression algorithm to create the model.
+The model estimates to probability of a certain response based on on or more features.
+[2] The model can be retrieved by training the bot against another player.
+The bot will use the model when playing the actual games.
+For more information on our implementation of the machine learning bots, refer to section 4.
+
+\clearpage
+\section{Research Question}
+In our research, we want to find \textit{what feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
+With improve the most, we mean as seen from the baseline.
+There is already a machine learning bot present, which will act as this base line.
+This bot has, what we will call the \textit{default feature space}- provided by the framework.
+\\
+
+\noindent
+The \textit{default feature space} contains the following features:
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\item Player 1's pending points
+\item Player 2's pending points
+\item The trump suit
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\end{itemize}
+
+\noindent
+Our goal is to build multiple bots machine learning bots, both with extended feature spaces and narrower feature spaces, and see which bot will improve most in relation to the default machine-learning bot.
+Our hypothesis is that the bots with an extended feature space will have a better performance the bots with a narrower feature space, and that the extended feature space bots will perform better than the default bot, where the narrow feature space will perform worse.
+This is because the narrowing of the feature space can cause underfitting, where the model 'cannot capture the underlying structure of the data'[3] increasing the chance of making a wrong prediction.
+Consequently, extending the feature space can cause overfitting, where the model has more features than the data needs, which can also lead to making the wrong predictions.
+
+\clearpage
+\section{Experimental setup}
+For the purpose of our research, we created 5 machine-learning bots accompanying the original machine-learning bot, each competing in multiple 120 game Schnapsen tournaments against each individual non-learning bot.
+All bots were trained and tested in the same way.
+Below, we will give an overview of the bots and the changes made with respect to the default machine-learning bot.
+For the whole overview, refer to appendix A.
+After that, we will describe the testing procedure.
+
+\subsection{The bots}
+The non- learning opponents were Rand, Bully and Rdeep. The learning bots we created were:
+\begin{description}
+\item [ml\_minimal:] This bot has the smallest feature space of all: only the perspective and the point count of both player 1 and player 2 as features.
+We wanted to see if a bot can still perform well, even if it just has minimal amount of information about the game state.
+
+\item [ml\_stripped:] ml\_stripped has almost all the features of the \textit{default feature space} except for both players pending points and trumpsuit id.
+
+\item [ml:] This ml bot is provided by the framework and consists of the  \textit{default feature space}
+
+\item [ml\_enriched:]  This bot has a slightly extended feature space in comparison to the original ml-bot. The following features were added to the feature space:
+\begin{itemize}
+\item Both player's points squared
+\item Both player's pending points squared
+\item Both player's points cubed
+\item Both player's pending points cubed
+\end{itemize}
+These features were added to go more to a design-matrix like feature space. Since the amount of points a player has are important for the game, we chose to focus solely on this.
+
+\item [ml\_advanced:] 
+This bot has a more extended feature space in addition to the \textit{default feature space}. Added are: 
+\begin{itemize}
+\item Difference between points
+\item Difference between pending points
+\item Trump card ratio in hand
+\item High card ratio in hand (10/A's)
+\item Number of trump cards in hand in phase 2
+\item Number of cards with same suit as opponents played suit
+\item Number of points in hand (squared)
+\end{itemize}
+This is the bot where we chose to add more of our own thought of features.
+Point difference was added, since this is a good indicator if a player is leading the game by a high margin.
+Furthermore, we chose to focus on both trump and high-ranking cards in the hand.
+The more you have, the better it is.
+The number of trump cards in phase 2 is also important: If you still got all your trump cards in phase 2 of the game, you have a high chance of beating your opponent.
+Furthermore the number of cards with same suit as opponents played suit feature was added, alongside the number of points in the player hand squared feature.
+
+\item[ml\_combined:] This bot has the most extended feature space. It combines the features of ml\_enriched and ml\_advanced.
+\end{description}
+\subsection{The testing procedure}
+
+Each learning bot played a total of 9 tournaments with 3 different models against each non-learning bot.
+The testing procedure was as follows:
+\begin{itemize}
+\item Training
+\item 120 Game tournament
+\item 120 Game tournament
+\item 120 Game tournament
+\end{itemize}
+
+This procedure was repeated twice to reach the total of 9 tournaments respectively.
+The testing only occurred between learning and non-learning bots.
+The learning bots did not compete against each other.
+In case of Rand and Bully, each training process consisted of 100,000 observations of the (non-learning) opponent.
+Rdeep was only observed 10,000 times during training, since training this bot takes a substantial amount of time.
+The margin of error we adhere is 5\%.
+\clearpage
+\section{Results}
+The tournament results are presented in Table 1.
+
+\setlength{\leftmargin}{0pt}
+\begin{center}
+  \begin{tabular}{ | l | l l | l l | l l | |l l | }
+     \hline
+      & \textbf{rand} & & \textbf{bully} & & \textbf{rdeep} & & \textbf{Total} & \\
+      & wins & losses & wins & losses & wins & losses  & wins & losses \\ \hline
+      ml\_minimal & 843 & 237 & 837 & 243 & 348 & 732 & 2028 & 1212 \\ \hline
+      ml\_stripped & 736 & 344 & 843 & 237 & 283 & 797 & 1862 & 1378 \\ \hline
+      ml & 866 & 214 & 876 & 204 & 257 & 823 & 1999 & 1241 \\ \hline 
+      ml\_enriched & 881 & 119 & 772 & 308 & 284 & 798 & 1937 & 1303 \\ \hline
+      ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
+      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806  & 1982 & 1258\\ \hline
+  \end{tabular}
+\end{center}
+\textbf{Table 1}: Overview of tournament wins and losses per ml-bot. \\
+
+\begin{center}
+\begin{tabular}{| r | r | r | r || r |}
+\hline
+      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
+      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
+      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
+      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
+      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
+      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
+      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
+\end{tabular} \\
+\end{center}
+
+\textbf{Table 2}: Improvement over ml. \\
+\begin{center}
+\begin{tabular}{| r | r | r | r |}
+\hline
+      & \textbf{rand} & \textbf{bully} & \textbf{rdeep}\\ \hline
+      Standard deviation & 0.0652 & 0.0432 & 0.0280    \\ \hline
+\end{tabular} \\
+\end{center}
+
+\textbf{Table 3}: \textit{Standard deviation} of the mean of the 9 tournaments for each bot. \\
+
+\begin{center}
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\linewidth]{images/barplotRand.png}
+\captionof{figure}{Part of games won against Rand}
+\end{minipage}
+\hfill
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\linewidth]{images/barplotBully.png}
+\captionof{figure}{Part of games won against Bully}
+\end{minipage}
+      \\ %extra line for space
+\begin{minipage}{0.49\linewidth}
+\includegraphics[width=\linewidth]{images/barplotRdeep.png}
+\captionof{figure}{Part of games won against Rdeep (please notice the Y-axis)}
+\end{minipage}
+\end{center}
+
+\section{Findings}
+
+\subsection*{Against Rand}
+There are a few notable things when comparing the performance of our bots.
+Firstly, while both ml\_minimal and ml\_stripped performed slightly worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal.
+Despite the latter of the two having the smallest feature set.
+However, the differences are below 5\% and therefore within the margin of error.
+Secondly, stripping away most of the feature set in ml\_minimal only led to a relatively small performance loss.
+Lastly, ml\_enriched and ml\_advanced perform, respectively, a little better and a little worse when compared to the stock ml bot.
+However, when we combined the feature sets of these two bots in ml\_combined, it led to an performance increase of almost 10\% compared to the stock ml bot.
+In short, the bots with the larger feature spaces did perform relatively better against rand.
+
+\subsection*{Against Bully}
+
+Notable for the results of the tournaments against the bully bot are the following points.
+First of all, the stock ml bot performed the best of all bots.
+In figure 2 this is clearly noticable.
+Secondly,  ml\_stripped and ml\_minimal peformed comparable to ml bot.
+Therefore, we may conclude the smaller feature spaces do not cause a heavy impact on the performance of a learning bot.
+The last and most remarkable finding is the peformance of the ml\_enriched and ml\_combined bots.
+All bots with larger feature spaces peformed worse than ml bot.
+However, ml\_enriched and ml\_combined performed the worst with a performance decrease of approximately 9\%.
+
+\subsection*{Against Rdeep}
+The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.0280.
+This number is the lowest of all the non-learning bots and is clearly confirmed by the barplot in figure 3.
+Rdeep won the majority of the games, which results in a low diversity of winning scores among the learning bots.
+The worst performer was, surprisingly, the stock ml bot.
+Although the variance in the winning scores is low, the ml\_minimal bot performs clearly better against rdeep.
+Compared to the other learning bots, ml\_minimal performs approximately 25\% better.
+Also remarkable is the relatively low score of ml\_combined with the most features of all.
+The other bots containing a larger feature space did perform slightly better than the stock ml bot, although this is all within the margin of error.
+Summarized, the bots with the smallest featurespaces seemed to perform the best against rdeep.
+
+\section{Conclusion}
+Performance is different per bot, and we can not say a lot since we do not have the data to do so , not enough data blabalablalbalalb
+
+\section{References}
+1. http://humanparagon.com/strong-and-weak-ai/
+2. https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f
+3. https://en.wikipedia.org/wiki/Overfitting
+
+\clearpage
+\section{Appendix}
+\subsection{Overview of machine-learning bots' feature spaces}
+\subsection{ml\_minimal}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\end{itemize}
+\subsection{ml\_stripped}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\end{itemize}
+\subsection{ml\_enriched}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 1's point count squared
+\item Player 1's point count cubed
+\item Player 2's point count
+\item Player 2's point count squared
+\item Player 2's point count cubed
+\item Player 1's pending points
+\item Player 1's pending points squared
+\item Player 1's pending points cubed
+\item Player 2's pending points
+\item Player 2's pending points squared
+\item Player 2's pending points cubed
+\item The trump suit
+\item The phase
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\end{itemize}
+\subsection{ml\_advanced}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 2's point count
+\item Player 1's pending points
+\item Player 2's pending points
+\item Difference between player 1 and player 2's point count
+\item Difference between player 1 and player 2's pending point count
+\item The trump suit
+\item Trump card ratio (Number of trump cards in hand / total number of cards in hand * 100)
+\item High-ranking card ratio (Number of 10's and A's in hand / total number of cards in hand * 100)
+\item The phase
+\item Number of trump cards in hand in phase 2
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\item Number of cards in same suit as opponent's played suit in hand.
+\item Number of points in hand squared ($card1^2$ + $card2^2$ ...)
+\end{itemize}
+
+\subsection{ml\_combined}
+\begin{itemize}
+\item Perspective information
+\item Player 1's point count
+\item Player 1's point count squared
+\item Player 1's point count cubed
+\item Player 2's point count
+\item Player 2's point count squared
+\item Player 2's point count cubed
+\item Player 1's pending points
+\item Player 1's pending points squared
+\item Player 1's pending points cubed
+\item Player 2's pending points
+\item Player 2's pending points squared
+\item Player 2's pending points cubed
+\item Difference between player 1 and player 2's point count
+\item Difference between player 1 and player 2's pending point count
+\item The trump suit
+\item Trump card ratio (Number of trump cards in hand / total number of cards in hand * 100)
+\item High-ranking card ratio (Number of 10's and A's in hand / total number of cards in hand * 100)
+\item The phase
+\item Number of trump cards in hand in phase 2
+\item The stock size
+\item The leader
+\item Whose turn it is currently
+\item The played card of the opponent
+\item Number of cards in same suit as opponent's played suit in hand.
+\item Number of points in hand squared ($card1^2$ + $card2^2$ ...)
+\end{itemize}
+
+\section{Worksheet I}
+\begin{enumerate}
+
+\item The \textit{rdeep} bot performs best, winning 20 out of 30 games. \\
+Output:
+\begin{lstlisting}[language=bash]
+Results:
+bot <bots.rand.rand.Bot instance at 0x101a70fc8>: 7 wins
+bot <bots.bully.bully.Bot instance at 0x101a71098>: 3 wins
+bot <bots.rdeep.rdeep.Bot instance at 0x101a71170>: 20 wins
+\end{lstlisting}
+
+\item The bully bot operates as follows:
+\begin{itemize}
+\item If it has a trump card, it will play that.
+\item If it does not have a trump card, it will play a card from the same suit
+\item If it cannot do either of those things, it will choose the highest ranking card of any suit.
+\end{itemize}
+
+\item Using this strategy means that you will try to get as many points as possible each move.
+However, this might also mean that early in the game, the bot will play valuable cards in order to get a high point ratio, but later in the game it has no good cards left.
+
+\item Have the bots complete a large number of tournaments (preferably n > 30), see if the rdeep bot still outperforms the rand bot, and how big the difference in wins is.
+If there is a significant difference, we can assume that rdeep is better than rand.
+
+\item MyBot implementation:
+It plays any available trump card first. If none is available it picks a random card.
+
+\begin{lstlisting}[language=bash]
+def get_move(self, state):
+        moves = state.moves()
+        return get_trump_card(moves,state)
+def get_trump_card(moves,state):
+    randomChoice = random.choice(moves)
+    counter = 0
+    if randomChoice == None:
+        print "NONE FOUND"
+    if moves == None:
+        print "None available"
+        return None
+    while True:
+        randomChoice = random.choice(moves)
+        counter +=1
+        if randomChoice == None:
+            print "NONE returned"
+            return randomChoice
+        try:
+            if util.get_suit(randomChoice[0]) 
+            == State.get_trump_suit(state):
+                #print "Playing trump card"
+                return randomChoice
+        except:
+            #print "KEY ERROR"
+            pass
+        if counter > 40 and not randomChoice == None:
+            #print "Playing normal card"
+            return randomChoice
+    return randomChoice
+\end{lstlisting}
+
+When no legal moves are to be made except the best trump card you have no legal moves when you  remove the trump card from the list of legal moves.
+In that case the python program expects a move but it gets a return type "None".
+That's why it raises an error.
+
+Output:
+\begin{lstlisting}[language=bash]
+Results:
+    bot <bots.rand.rand.Bot instance at 0x7fe73586fab8>: 25 wins
+    bot <bots.mybot.mybot.Bot instance at 0x7fe73587a440>: 45 wins
+\end{lstlisting}
+
+\item The heat map:
+- Insert pdf here - This heatmap means:
+If player 2 has a high non-move probability, this is better for player 1 if player 1 has a low-non move probability.
+Both players seem to have a good value if the non-move probability is around 0.4 - 0.6.
+
+\item The added line:
+\begin{lstlisting}[language=bash]
+value, move = self.value(next_state, depth + 1)
+\end{lstlisting}
+Output:
+\begin{lstlisting}[language=bash]
+python tournament.py -p rand,minimax -s 2 -r 10
+Playing 10 games:
+Played 1 out of 10 games (10%): [0, 1] 
+Played 2 out of 10 games (20%): [0, 2] 
+Played 3 out of 10 games (30%): [0, 3] 
+Played 4 out of 10 games (40%): [0, 4] 
+Played 5 out of 10 games (50%): [1, 4] 
+Played 6 out of 10 games (60%): [2, 4] 
+Played 7 out of 10 games (70%): [2, 5] 
+Played 8 out of 10 games (80%): [3, 5] 
+Played 9 out of 10 games (90%): [4, 5] 
+Played 10 out of 10 games (100%): [4, 6] 
+Results:
+bot <bots.rand.rand.Bot instance at 0x102a70f80>: 4 wins
+bot <bots.minimax.minimax.Bot instance at 0x102a731b8>: 6 wins
+\end{lstlisting}
+
+\item The added code:
+
+It creates one instance for each bot, minimax and alphabeta.
+Then in generates a state, and it does a few random moves.
+It measures the time to get the next move from both the minimax and alphabeta, then it compares the outcomes.
+If they are equal it will print "Agreed." else it will display the answers of both bots.
+This process is repeated a few times.
+Even though the code is right, the checking program does not behave correctly. That's why we do not have a valid output.
+
+\item The heuristic is a value between -1.0 and 1.0, derived from the point ratio of the current player.
+If the player has a 1.0 value, the player has a definite win.
+If the value is -1.0, the opponent has a definite win.
+
+We came up with, the ratio of trump cards in hand, it turned out to be a horrible heuristic.
+Holding on to your trumps seems to be a bad tactic.
+Therefore we tried ditching trumps as soon as possible, this lead to somewhat better results, but random was still a better bot in the end.
+
+\end{enumerate}
+\section{Worksheet II}
+\begin{enumerate}
+\item The added clause that makes the knowledge base unsatisfiable:
+\begin{lstlisting}[language=bash]
+kb.add_clause(~B, ~C)
+\end{lstlisting}
+
+\item The three clauses converted to CNF:
+\begin{itemize}
+\item A V B
+\item -B V A
+\item -A V C
+\item -A V D
+\end{itemize}
+The code that creates the variables and the knowledge base:
+\begin{lstlisting}[language=bash]
+# Define our symbols
+A = Boolean('A')
+B = Boolean('B')
+C = Boolean('C')
+D = Boolean('D')
+
+# Create a new knowledge base
+kb = KB()
+
+# Add clauses
+kb.add_clause(A, B)
+kb.add_clause(~B, A)
+kb.add_clause(~A, C)
+kb.add_clause(~A, D)
+\end{lstlisting}
+Because the knowledge base entails A \& C \& D, all three have to be true. For now, the model has two solutions:
+\begin{lstlisting}[language=bash]
+{A: True, C: True, B: False, D: True}
+{A: True, C: True, B: True, D: True}
+\end{lstlisting}
+B can be whatever it wants, but A, B and D have to be true.
+
+\item Three constraints have to be met:
+\begin{enumerate}[I]
+\item $X = Y$
+\item $X + Y > 2$
+\item $X + Y < 5$
+\end{enumerate}
+The model is satisfiable, as long as: 
+$1 < x < 2.5$ and $1 < y < 2.5$
+
+\item We now have three models:
+\begin{lstlisting}[language=bash]
+(a) [x = y] = True, [x + y > 2] = True, [x + y < 5] = True
+(b) [x = y] = True, [x + y > 2] = True, [x + y < 5] = False
+(c) [x = y] = True, [x + y > 2] = False, [x + y < 5] = True
+\end{lstlisting}
+
+The three constraints per model: \\\\
+(a) This model already has three constraints. \\
+(b) Only the last clause has to change, namely to $[x + y >=5] $= True\\
+(c) Only the second clause has to change, namely to$ [x + y <= 2]$ = True.\\
+
+Now we end up with this:
+\begin{lstlisting}[language=bash]
+(a) [x = y] = True, [x + y > 2] = True, [x + y < 5] = True
+(b) [x = y] = True, [x + y > 2] = True, [x + y >= 5] = True
+(c) [x = y] = True, [x + y <= 2] = True, [x + y < 5] = True
+\end{lstlisting}
+
+\item What we want, is to find points on the line $x = y$, where the points either lie between $x + y > -5$ and $x + y < -2$, or where the points lie between $x + y > 2$ and $x + y < 5$.
+
+The clauses we need to add are:
+\begin{itemize}
+\item $x == y$
+\item $x + y > 2 V  x + y < -2$
+\item $x + y > -5 V  x + y < 5$
+\item $x + y > - 5 V  x + y > 2$
+\item $x + y < -2 V  x + y < 5$
+\end{itemize}
+
+The code:
+\begin{lstlisting}[language=bash]
+# Define our integer symbols
+x = Integer('x')
+y = Integer('y')
+
+q = x == y
+a = x + y > 2
+b = x + y < 5
+c = x + y < -2
+d = x + y > -5
+
+kb = KB()
+
+kb.add_clause(q)
+kb.add_clause(a, c)
+kb.add_clause(a, d)
+kb.add_clause(b, c)
+kb.add_clause(b, d)
+\end{lstlisting}
+
+\item 6)The playing ace strategy work:
+
+\begin{lstlisting}[language=bash]
+kb.add_clause(A0)
+kb.add_clause(A5)
+kb.add_clause(A10)
+kb.add_clause(A15)
+
+#PLAY ACE STRATEGY
+kb.add_clause(~A0, PA0)
+kb.add_clause(~A5, PA5)
+kb.add_clause(~A10, PA10)
+kb.add_clause(~A15, PA15)
+kb.add_clause(~PA0, A0)
+kb.add_clause(~PA5, A5)
+kb.add_clause(~PA10, A10)
+kb.add_clause(~PA15, A15)
+\end{lstlisting}
+
+When adding: 
+\begin{lstlisting}[language=bash]
+kb.add_clause(~PA0)
+\end{lstlisting}
+The statisfiability with the KB fails, therefore we know PA0 is entailed by the KB
+
+\item We implemented the PlayCheap strategy:
+
+\item Game output
+
+\item 
+\end{enumerate}
+\section{Worksheet III}
+\begin{enumerate}
+\item The added code:
+\begin{lstlisting}[language=bash]
+value = self.heuristic(next_state)
+
+p1_points = state.get_points(1)
+
+p2_points = state.get_points(2)
+
+p1_pending_points = state.get_pending_points(1)
+
+p2_pending_points = state.get_pending_points(2)
+
+trump_suit = state.get_trump_suit()
+
+phase = state.get_phase()
+
+stock_size = state.get_stock_size()
+
+leader = state.leader()
+
+whose_turn = state.whose_turn()
+
+opponents_played_card = state.get_opponents_played_card()
+\end{lstlisting}
+The result of the played tournament against rand and bully:
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102271290>: 16 wins
+bot <bots.rand.rand.Bot instance at 0x1022711b8>: 4 wins
+bot <bots.bully.bully.Bot instance at 0x1059b71b8>: 10 wins
+\end{lstlisting}
+
+\item We let the mlbot learn by playing against rdeep. But since the games took way longer than the games of mlbot vs rand, we set the number of games to 1000 (Which still took quite some time).
+
+We get a lower output now:
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102a73248>: 15 wins
+bot <bots.rand.rand.Bot instance at 0x102a73170>: 7 wins
+bot <bots.bully.bully.Bot instance at 0x10599df80>: 8 wins
+\end{lstlisting}
+
+ML now wins 15 times, where it won 16 times on the first tournament.
+This might have to do with the training set being smaller, and it was trained against rdeep, which does not compete in the tournament.
+However, the difference is not comparably worse.
+
+We decided to train the mlbot again against rdeep, but now with 5000 games. 
+Even after this long wait, the robot does not play significantly better or worse.
+
+\begin{lstlisting}[language=bash]
+bot <bots.ml.ml.Bot instance at 0x102a71248>: 14 wins
+bot <bots.rand.rand.Bot instance at 0x102a71170>: 5 wins
+bot <bots.rdeep.rdeep.Bot instance at 0x105aa2cf8>: 11 wins
+\end{lstlisting}
+
+\item We created three ml bots:
+\begin{itemize}
+\item The first one was trained on rdeep
+\item The second one was trained on rand
+\item The third one was trained on the second bot.
+\end{itemize}
+
+We played a tournament with 300 games in total. The results:
+\begin{lstlisting}[language=bash]
+    bot <bots.ml.ml.Bot instance at 0x10ad81ef0>: 92 wins
+    bot <bots.ml.ml.Bot instance at 0x10ad81f80>: 99 wins
+    bot <bots.ml.ml.Bot instance at 0x10b80cb00>: 109 wins
+\end{lstlisting}
+As you can see, bot 3 only performed a bit better than the other two, but there is no really significant difference between the bots.
+
+\item For added features, read this research paper. It's all about added features.
+
+\end{enumerate}
+=======
 \documentclass[a4paper,11pt]{article}
@@
 \end{enumerate}
+>>>>>>> 84a742d35e719823e996e26633d936ee2353a31e
 \end{document}

### 2018-02-01 Text/paper.tex
Fixed unfixed merge conflict in paper.tex

--- 2018-02-01 Text/paper.tex
@@
 \subsection{Overview of machine-learning bots' feature spaces}
-\subsection{ml\_minimal}
+\begin{description}
+\item[ml\_minimal]
 \begin{itemize}
@@
 \end{itemize}
-
+\end{description}
 \section{Worksheet I}

### 2018-02-01 Text/paper.tex
Improved layout
Added conclusion

@@
 \usepackage{enumerate}
-\usepackage{graphicx} % Required for including images
+\usepackage{graphicx}
+\usepackage{hyperref}
 \usepackage[font=small,labelfont=bf]{caption}
@@
 \begin{document}
+
+\begin{titlepage}
+
+\centering
 \maketitle
+\includegraphics[width=0.8\linewidth]{images/vulogo.png}
+\pagenumbering{gobble} %pagenumbering OFF
+
+\end{titlepage}
 \clearpage
+
+\tableofcontents
+\clearpage
+
+\pagenumbering{arabic} %pagenumbering ON
 
@@
 
-The game has a multi-agent (we have an opponent), deterministic (the environment is determined by the current state and executed action), static (the environment does not change when an agent is choosing an action) and discrete (the game is turn-based) environment.
+The game has a multi-agent (we have an opponent), deterministic (the environment is determined by the current state and executed action), static (the environment does not change when an agent is choosing an action) and discrete (the game is turn-based) environment [2].
 The game consists of two phases: In phase one, when there are still cards in stock, we have an imperfect information game.
@@
 The model estimates to probability of a certain response based on on or more features.
-[2] The model can be retrieved by training the bot against another player.
+[3] The model can be retrieved by training the bot against another player.
 The bot will use the model when playing the actual games.
@@
 Our hypothesis is that the bots with an extended feature space will have a better performance the bots with a narrower feature space, and that the extended feature space bots will perform better than the default bot, where the narrow feature space will perform worse.
-This is because the narrowing of the feature space can cause underfitting, where the model 'cannot capture the underlying structure of the data'[3] increasing the chance of making a wrong prediction.
+This is because the narrowing of the feature space can cause underfitting, where the model 'cannot capture the underlying structure of the data [4] increasing the chance of making a wrong prediction.
 Consequently, extending the feature space can cause overfitting, where the model has more features than the data needs, which can also lead to making the wrong predictions.
@@
 
+In Table 2, we see the performance improvement (if applicable) over the default ml-bot.
 \begin{center}
@@
 \textbf{Table 2}: Improvement over ml. \\
+
+In Table 3, we see the standard deviations of the mean of the 9 tournaments per bot.
+
 \begin{center}
@@
 \textbf{Table 3}: \textit{Standard deviation} of the mean of the 9 tournaments for each bot. \\
+
+Below, we present three bar plots, with the part of games won by the ml-bots against rand, bully and rdeep in Figure 1,2 and 3 respectively. \\
+\textbf{NB:} The y-axis scale in figure three is different from figure 1 and 2.
 
@@
 \includegraphics[width=\linewidth]{images/barplotRdeep.png}
-\captionof{figure}{Part of games won against Rdeep (please notice the Y-axis)}
+\captionof{figure}{Part of games won against Rdeep (mind the different Y-axis)}
 \end{minipage}
 \end{center}
-
+\clearpage
 \section{Findings}
@@
 First of all, the stock ml bot performed the best of all bots.
-In figure 2 this is clearly noticable.
+In figure 2 of section 5, this is clearly noticable.
 Secondly,  ml\_stripped and ml\_minimal peformed comparable to ml bot.
-Therefore, we may conclude the smaller feature spaces do not cause a heavy impact on the performance of a learning bot.
+Therefore, we may observe that smaller feature spaces seem to not cause a heavy impact on the performance of a learning bot.
 The last and most remarkable finding is the peformance of the ml\_enriched and ml\_combined bots.
 All bots with larger feature spaces peformed worse than ml bot.
-However, ml\_enriched and ml\_combined performed the worst with a performance decrease of approximately 9\%.
+However, ml\_enriched and ml\_combined performed the worst with a performance decrease of approximately 12\%.
 
@@
 The other bots containing a larger feature space did perform slightly better than the stock ml bot, although this is all within the margin of error.
-Summarized, the bots with the smallest featurespaces seemed to perform the best against rdeep.
+Summarized, the bots with the smallest feature spaces seemed to perform the best against rdeep.
 
 \section{Conclusion}
-Performance is different per bot, and we can not say a lot since we do not have the data to do so , not enough data blabalablalbalalb
+In this paper, we set out to find performance improvements in machine-learning bots  playing the game of Schnapsen when using different feature spaces by comparing multiple machine learning bots, each bot equipped with its own extended or narrowed feature space.
+We observed that with all the different models we tried, there is not a huge performance increase.
+Overall, most bots even perform a bit worse than the default ml-bot.
+Only in the games against rdeep, all bots performed better than the default-ml, with a quite big margin.
+Even then, the bots with a narrowed feature space perform better than the bots with an extended feature space.
+This gives rise to the question: Does extending the feature space in this kind of machine learning bot actually have benefits?
+It seems that after this research, more questions have risen than have been answered.
+We cannot really say that we have found an overall performance increase in any bot, only performance increase against specific bots.
+Unfortunately, we cannot answer our research question now, because of the limited time we had.
+There seems to be no findable correlation between feature space and game performance in the data.
+We did see some improvement over the default ml-bot, but only in very small amounts.
+In future research, we would hold way more tournaments with more bots, looking at features one on one, to see which improve and which decrease performance.
 
 \section{References}
-1. http://humanparagon.com/strong-and-weak-ai/
-2. https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f
-3. https://en.wikipedia.org/wiki/Overfitting
+1. http://humanparagon.com/strong-and-weak-ai/ \\
+2. Lecture 4 of Intelligent Systems, VU, 2018 - \url{https://www.youtube.com/watch?v=nFfjcGKziQE&index=17&list=UUyRRg2ERDkUWKd2p3_KVidA} \\
+3. https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f \\
+4. https://en.wikipedia.org/wiki/Overfitting
 
@@
 \item[ml\_minimal]
+
 \begin{itemize}
+
 \item Perspective information

### 2018-02-01 Text/paper.tex
Finished paper!!!

@@
 
-\title{The benefits of an extended feature space in a machine learning bot for the game Schnapsen}
+\title{Comparing the perfomance impacts of narrow and extended feature spaces in machine learning bots in the game of Schnapsen}
 \date{January 25, 2018}
@@
 These bots were trained multiple times, and played multiple tournaments against multiple other bots.
-The results are..
+The results were analyzed using statistics, but they did not show a substantial improvement or decrease of performance.
+There seems to be a small performance increase against specific bots, but no significant overall increase.
+We concluded that we need more extensive research to gain insight in performance of the different feature spaces.
 \end{abstract}
@@
 \section{Research Question}
-In our research, we want to find \textit{what feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
+In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
 With improve the most, we mean as seen from the baseline.

### 2018-02-01 Text/paper.tex
title fix
changed in to for
Added 2 pagebreaks for layout
added bibliography and fixed layout of appendix (gone with merging)

@@
 
-\title{Comparing the perfomance impacts of narrow and extended feature spaces in machine learning bots in the game of Schnapsen}
+\title{Comparing the perfomance impacts of narrow and extended feature spaces for machine learning bots in the game of Schnapsen}
 \date{January 25, 2018}
@@
 
+\clearpage
 \item [ml\_advanced:] 
@@
 \section{References}
-1. http://humanparagon.com/strong-and-weak-ai/ \\
-2. Lecture 4 of Intelligent Systems, VU, 2018 - \url{https://www.youtube.com/watch?v=nFfjcGKziQE&index=17&list=UUyRRg2ERDkUWKd2p3_KVidA} \\
-3. https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f \\
-4. https://en.wikipedia.org/wiki/Overfitting
+
+\begin{enumerate}
+\item What's The Difference Between Strong and Weak AI?, \url{http://humanparagon.com/strong-and-weak-ai/}.
+
+\item Schlobach, S.: Intelligent Systems 2018 L4P2 More on Informed Search, \url{https://www.youtube.com/watch?v=nFfjcGKziQE}.
+
+\item Chandrayan, P.: Machine Learning Part 3 : Logistic Regression – Towards Data Science, \url{https://towardsdatascience.com/machine-learning-part-3-logistics-regression-9d890928680f}.
+
+\item Overfitting, \url{https://en.wikipedia.org/wiki/Overfitting}.\\
+
+\end{enumerate}
 
@@
 \begin{description}
-\item[ml\_minimal]
-
+\item[ml\_minimal] \hfill
 \begin{itemize}
-
 \item Perspective information
@@
 \end{itemize}
-\subsection{ml\_stripped}
+\item[ml\_stripped] \hfill
 \begin{itemize}
@@
 \end{itemize}
-\subsection{ml\_enriched}
+\item[ml\_enriched] \hfill
 \begin{itemize}
@@
 \end{itemize}
-\subsection{ml\_advanced}
+\item[ml\_advanced] \hfill
 \begin{itemize}
@@
 
-\subsection{ml\_combined}
+\item[ml\_combined] \hfill
 \begin{itemize}
@@
 \end{description}
-\section{Worksheet I}
+\subsection{Worksheet I}
 \begin{enumerate}
@@
 \end{enumerate}
-\section{Worksheet II}
+\subsection{Worksheet II}
 \begin{enumerate}
@@
 \end{enumerate}
-\section{Worksheet III}
+
+\clearpage
+\subsection{Worksheet III}
 \begin{enumerate}

### 2018-02-01 Text/paper.tex
Final version of the paper and added inverse kbbot (play expensive)

@@
 \title{Comparing the perfomance impacts of narrow and extended feature spaces for machine learning bots in the game of Schnapsen}
-\date{January 25, 2018}
+\date{January 27, 2018}
 \author{Lucas Faijdherbe, Daan Schrage and Ruben van der Ham\\\\
@@
 \section{Research Question}
-In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
+In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance in the game of Schnapsen}.
 With improve the most, we mean as seen from the baseline.
@@
 \end{description}
+
+\clearpage
 \subsection{Worksheet I}
@@
 \item We implemented the PlayCheap strategy:
+\begin{lstlisting}[language=bash]
+    kb.add_clause(~PC2, J2, Q2, K2)
+    kb.add_clause(~J2, PC2)
+    kb.add_clause(~Q2, PC2)
+    kb.add_clause(~K2, PC2)
 
-\item Game output
+    kb.add_clause(~PC3, J3, Q3, K3)
+    kb.add_clause(~J3, PC3)
+    kb.add_clause(~Q3, PC3)
+    kb.add_clause(~K3, PC3)
 
-\item 
+    kb.add_clause(~PC4, J4, Q4, K4)
+    kb.add_clause(~J4, PC4)
+    kb.add_clause(~Q4, PC4)
+    kb.add_clause(~K4, PC4)
+
+    kb.add_clause(~PC7, J7, Q7, K7)
+    kb.add_clause(~J7, PC7)
+    kb.add_clause(~Q7, PC7)
+    kb.add_clause(~K7, PC7)
+
+    kb.add_clause(~PC8, J8, Q8, K8)
+    kb.add_clause(~J8, PC8)
+    kb.add_clause(~Q8, PC8)
+    kb.add_clause(~K8, PC8)
+
+    kb.add_clause(~PC9, J9, Q9, K9)
+    kb.add_clause(~J9, PC9)
+    kb.add_clause(~Q9, PC9)
+    kb.add_clause(~K9, PC9)
+
+    kb.add_clause(~PC12, J12, Q12, K12)
+    kb.add_clause(~J12, PC12)
+    kb.add_clause(~Q12, PC12)
+    kb.add_clause(~K12, PC12)
+
+    kb.add_clause(~PC13, J13, Q13, K13)
+    kb.add_clause(~J13, PC13)
+    kb.add_clause(~Q13, PC13)
+    kb.add_clause(~K13, PC13)
+
+    kb.add_clause(~PC14, J14, Q14, K14)
+    kb.add_clause(~J14, PC14)
+    kb.add_clause(~Q14, PC14)
+    kb.add_clause(~K14, PC14)
+
+    kb.add_clause(~PC17, J17, Q17, K17)
+    kb.add_clause(~J17, PC17)
+    kb.add_clause(~Q17, PC17)
+    kb.add_clause(~K17, PC17)
+
+    kb.add_clause(~PC18, J18, Q18, K18)
+    kb.add_clause(~J18, PC18)
+    kb.add_clause(~Q18, PC18)
+    kb.add_clause(~K18, PC18)
+
+    kb.add_clause(~PC19, J19, Q19, K19)
+    kb.add_clause(~J19, PC19)
+    kb.add_clause(~Q19, PC19)
+    kb.add_clause(~K19, PC19)
+\end{lstlisting}
+
+\item Game output:
+\begin{lstlisting}[language=bash]
+   Start state: The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD JH
+Player 2's hand: AC KC AD QH 10S
+There are 10 cards in the stock
+
+player1: <bots.kbbot.kbbot.Bot instance at 0x7f1506109998>
+player2: <bots.rand.rand.Bot instance at 0x7f1506109ef0>
+*   Player 1 plays: JH
+The game is in phase: 1
+Player 1's points: 0, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD JH
+Player 2's hand: AC KC AD QH 10S
+There are 10 cards in the stock
+Player 1 has played card: J of H
+
+*   Player 2 plays: 10S
+The game is in phase: 1
+Player 1's points: 12, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD QD
+Player 2's hand: AC KC AD QH AS
+There are 8 cards in the stock
+
+*   Player 1 plays: QD
+*   Player 1 melds a marriage between QD and KD
+The game is in phase: 1
+Player 1's points: 12, pending: 20
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD QD
+Player 2's hand: AC KC AD QH AS
+There are 8 cards in the stock
+Player 1 has played card: Q of D
+
+*   Player 2 plays: KC
+The game is in phase: 1
+Player 1's points: 39, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD AH
+Player 2's hand: AC AD QH AS KS
+There are 6 cards in the stock
+
+*   Player 1 plays: KD
+The game is in phase: 1
+Player 1's points: 39, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D KD AH
+Player 2's hand: AC AD QH AS KS
+There are 6 cards in the stock
+Player 1 has played card: K of D
+
+*   Player 2 plays: AS
+The game is in phase: 1
+Player 1's points: 54, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC JC 10D AH
+Player 2's hand: AC AD KH QH KS
+There are 4 cards in the stock
+
+*   Player 1 plays: JC
+The game is in phase: 1
+Player 1's points: 54, pending: 0
+Player 2's points: 0, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC JC 10D AH
+Player 2's hand: AC AD KH QH KS
+There are 4 cards in the stock
+Player 1 has played card: J of C
+
+*   Player 2 plays: QH
+The game is in phase: 1
+Player 1's points: 54, pending: 0
+Player 2's points: 5, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D JD AH
+Player 2's hand: AC AD KH KS QS
+There are 2 cards in the stock
+
+*   Player 2 plays: QS
+The game is in phase: 1
+Player 1's points: 54, pending: 0
+Player 2's points: 5, pending: 0
+The trump suit is: H
+Player 1's hand: 10C QC 10D JD AH
+Player 2's hand: AC AD KH KS QS
+There are 2 cards in the stock
+Player 2 has played card: Q of S
+
+*   Player 1 plays: QC
+The game is in phase: 2
+Player 1's points: 54, pending: 0
+Player 2's points: 11, pending: 0
+The trump suit is: H
+Player 1's hand: 10C 10D JD AH 10H
+Player 2's hand: AC AD KH KS JS
+There are 0 cards in the stock
+
+*   Player 2 plays: KS
+The game is in phase: 2
+Player 1's points: 54, pending: 0
+Player 2's points: 11, pending: 0
+The trump suit is: H
+Player 1's hand: 10C 10D JD AH 10H
+Player 2's hand: AC AD KH KS JS
+There are 0 cards in the stock
+Player 2 has played card: K of S
+
+*   Player 1 plays: 10H
+The game is in phase: 2
+Player 1's points: 68, pending: 0
+Player 2's points: 11, pending: 0
+The trump suit is: H
+Player 1's hand: 10C 10D JD AH
+Player 2's hand: AC AD KH JS
+There are 0 cards in the stock
+
+Game finished. Player 1 has won, receiving 2 points.
+\end{lstlisting}
+\item Game output of tournament kbbot with 'cheap strategy' and kbbot inverse with 'play expensive' strategy:
+\begin{lstlisting}[language=bash]
+Playing 120 games:
+Results:
+    bot <bots.kbbotinverse.kbbotinverse.Bot .......>: 64 wins
+    bot <bots.kbbot.kbbot.Bot ......>: 56 wins
+\end{lstlisting}
 \end{enumerate}

### 2018-02-01 bots/kbbotinverse/kbbotinverse.py

@@ -1,0 +1,71 @@
+#!/usr/bin/env python
+"""
+This is a bot that applies propositional logic reasoning to determine its strategy.
+The strategy it uses is determined by what is defined in load.py. Here it is to always
+pick a Jack to play whenever this is a legal move.
+
+It loads general information about the game, as well as the definition of a strategy,
+from load.py.
+"""
+
+from api import State, util
+import random, load
+
+from kb import KB, Boolean, Integer
+
+class Bot:
+
+    def __init__(self):
+        pass
+
+    def get_move(self, state):
+
+        moves = state.moves()
+
+        random.shuffle(moves)
+
+        for move in moves:
+
+            if not self.kb_consistent(state, move):
+                # Plays the first move that makes the kb inconsistent. We do not take
+                # into account that there might be other valid moves according to the strategy.
+                # Uncomment the next line if you want to see that something happens.
+                #print "Strategy Applied"
+                return move
+
+        # If no move that is entailed by the kb is found, play random move
+        return random.choice(moves)
+
+    # Note: In this example, the state object is not used,
+    # but you might want to do it for your own strategy.
+    def kb_consistent(self, state, move):
+    # type: (State, move) -> bool
+
+        # each time we check for consistency we initialise a new knowledge-base
+        kb = KB()
+
+        # Add general information about the game
+        load.general_information(kb)
+
+        # Add the necessary knowledge about the strategy
+        load.strategy_knowledge(kb)
+
+        # This line stores the index of the card in the deck.
+        # If this doesn't make sense, refer to _deck.py for the card index mapping
+        index = move[0]
+
+        # This creates the string which is used to make the strategy_variable.
+        # Note that as far as kb.py is concerned, two objects created with the same
+        # string in the constructor are equivalent, and are seen as the same symbol.
+        # Here we use "pj" to indicate that the card with index "index" should be played with the
+        # PlayJack heuristics that was defined in class. Initialise a different variable if 
+        # you want to apply a different strategy (that you will have to define in load.py)
+        variable_string = "pc" + str(index)
+        strategy_variable = Boolean(variable_string)
+
+        # Add the relevant clause to the loaded knowledge base
+        kb.add_clause(~strategy_variable)
+
+        # If the knowledge base is not satisfiable, the strategy variable is
+        # entailed (proof by refutation)
+        return not kb.satisfiable()

### 2018-02-01 bots/kbbotinverse/load.py

@@ -1,0 +1,238 @@
+from kb import KB, Boolean, Integer
+
+# Initialise all variables that you need for you strategies and game knowledge.
+# Add those variables here.. The following list is complete for the Play Jack strategy.
+J0 = Boolean('j0')
+J1 = Boolean('j1')
+J2 = Boolean('j2')
+J3 = Boolean('j3')
+J4 = Boolean('j4')
+J5 = Boolean('j5')
+J6 = Boolean('j6')
+J7 = Boolean('j7')
+J8 = Boolean('j8')
+J9 = Boolean('j9')
+J10 = Boolean('j10')
+J11 = Boolean('j11')
+J12 = Boolean('j12')
+J13 = Boolean('j13')
+J14 = Boolean('j14')
+J15 = Boolean('j15')
+J16 = Boolean('j16')
+J17 = Boolean('j17')
+J18 = Boolean('j18')
+J19 = Boolean('j19')
+# PJ0 = Boolean('pj0')
+# PJ1 = Boolean('pj1')
+# PJ2 = Boolean('pj2')
+# PJ3 = Boolean('pj3')
+# PJ4 = Boolean('pj4')
+# PJ5 = Boolean('pj5')
+# PJ6 = Boolean('pj6')
+# PJ7 = Boolean('pj7')
+# PJ8 = Boolean('pj8')
+# PJ9 = Boolean('pj9')
+# PJ10 = Boolean('pj10')
+# PJ11 = Boolean('pj11')
+# PJ12 = Boolean('pj12')
+# PJ13 = Boolean('pj13')
+# PJ14 = Boolean('pj14')
+# PJ15 = Boolean('pj15')
+# PJ16 = Boolean('pj16')
+# PJ17 = Boolean('pj17')
+# PJ18 = Boolean('pj18')
+# PJ19 = Boolean('pj19')
+
+Q0 = Boolean('q0')
+Q1 = Boolean('q1')
+Q2 = Boolean('q2')
+Q3 = Boolean('q3')
+Q4 = Boolean('q4')
+Q5 = Boolean('q5')
+Q6 = Boolean('q6')
+Q7 = Boolean('q7')
+Q8 = Boolean('q8')
+Q9 = Boolean('q9')
+Q10 = Boolean('q10')
+Q11 = Boolean('q11')
+Q12 = Boolean('q12')
+Q13 = Boolean('q13')
+Q14 = Boolean('q14')
+Q15 = Boolean('q15')
+Q16 = Boolean('q16')
+Q17 = Boolean('q17')
[…]

### 2018-02-01 Text/paper.tex
This is actually the final version of the paper.tex as handed in

@@
 \section{Research Question}
-In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance in the game of Schnapsen}.
+In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance the most in the game of Schnapsen}.
 With improve the most, we mean as seen from the baseline.
